---
title: "AD_Mathews"
author: "S/16/373_JAISHIEKA"
date: "1/3/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Loading the library**
```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(survival)
library(ggfortify)
library(survminer)
library(rms)
library(dynpred)
```
\
\
**Read the data set**
```{r, warning=FALSE,message=FALSE}
Home <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Home/Home.csv")
Overseas <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Overseas/Overseas.csv")
```
\
\
**Merge two data sets**
```{r, warning=FALSE,message=FALSE}
data_merge <- rbind(Home , Overseas)
```
\
\
**Filter the data of LD Chandimal**
```{r,warning=FALSE,message=FALSE}
bt2 <- data_merge %>% filter(grepl('AD Mathews' , Striker))
head(bt2)
```
\
\
**Head of specific columns**
```{r,warning=FALSE,message=FALSE}
bt2 %>% select(innings,cum_balls,wicket,cum_runs,cum_singles,cum_doubles,cum_boundaries,cum_dotBalls) %>% head()
```
\
\
**Coxph model stratified for different innings**
```{r,warning=FALSE,message=FALSE}
cox_AD_1 <- coxph(Surv(cum_balls , wicket) ~ cum_runs+cum_singles+cum_doubles+cum_boundaries+cum_dotBalls + strata(innings), data = bt2)
summary(cox_AD_1)
```
\
\
**Test for the proportional hazard assumptions**
```{r,warning=FALSE,message=FALSE}
test.ph.AD_1 <- cox.zph(cox_AD_1)
test.ph.AD_1
```
\
We can see that cum_single variable is violating the pH assumptions (p value is less than 0.05). Therefore we can use an extended cox model with two heaviside functions.
\
\
\
**Extended cox model**
\
\
**Split the dataset**
```{r,warning=FALSE,message=FALSE}
bt2_cut <- survSplit(bt2 , cut = 30 , end = "cum_balls" , event = "wicket" , start = "start" , id = "id")
```
\
We are splitting the data by the cut point as 30 balls.
\
\
**Create the heaviside function**
```{r,warning=FALSE,message=FALSE}
bt2_cut$hv1 <- bt2_cut$cum_singles * (bt2_cut$start < 30)
bt2_cut$hv2 <- bt2_cut$cum_singles * (bt2_cut$start >= 30)
```
\
**hv1** - When the number of balls faced is less than 30, hv1 is equal to cum_singles and when the number of balls faced is greater than 30, hv1 is equal to       zero.
\
\
**hv2** - When the number of balls faced is greater than 30, hv2 is equal to cum_singles and when the number of balls faced is less than 30, hv2 is equal to       zero.
\
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
cox_AD_new <- coxph(Surv(start,cum_balls , wicket) ~ 
                    cum_runs+hv1 + hv2 +cum_doubles+cum_boundaries+cum_dotBalls + cluster (id) + strata(innings), data = bt2_cut)
summary(cox_AD_new)
```
\
\
**Interpreting the hazard ratios (exp(coef))**
\
\
**cum_runs(0.64827)** - There is a 35% of decrease in the hazard when the number of runs increased by 1 from the current ball to the next ball to be faced.
\
\
**hv1 (0.09063)** - If the number of balls faced is less than 30, then there is a 91% of decrease in the hazard when the number of singles scored is                        increased by 1 from the current ball to the next ball to be faced.
\
\
**hv2 (0.11873)** - If the number of balls faced is greater than 30, then there is a 88% of decrease in the hazard when the number of singles scored is                     increased by 1 from the current ball to the next ball to be faced.
\
\
**cum_doubles(0.23058)** - There is a 77% of decrease in the hazard when the number of doubles scored is increased by 1 from the current ball to the                               next ball to be faced.
\
\
**cum_boundaries(0.52672)** - There is a 47% of decrease in the hazard when the number of boundaries scored is increased by 1 from the current ball to                                the next ball to be faced.
\
\
**cum_dotBalls(0.07237)** - There is a 93% of decrease in the hazard when the number of dot balls scored is increased by 1 from the current ball to the                            next ball to be faced.
\
\
We can see that the concordance is a high value and also the test statistics are statistically significant. Therefore we can say that this is a good model.
\
\
**Test the pH assumptions**
```{r,warning=FALSE,message=FALSE}
test.ph.AD_new <- cox.zph(cox_AD_new)
test.ph.AD_new
```
\
All the covariates and the global test are not statistically significant. Therefore we can say that the ph assumptions are not violated.
\
\
\

**Adjusted survival curve**
```{r,warning=FALSE,message=FALSE}
s2 <- ggadjustedcurves(cox_AD_new , data = bt2_cut , size = 2,ggtheme = theme_survminer()) + 
      geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") + 
      scale_x_continuous(breaks = seq(0,120,10)) + scale_y_continuous(breaks = seq(0,1,0.1))
s2
```
\
**Validate the model**
```{r,message=FALSE,warning=FALSE}
cox_ad_3 <- cph(Surv(start,cum_balls , wicket) ~ cum_runs+hv1 + hv2 +cum_doubles+cum_boundaries+cum_dotBalls + 
                  cluster (id) + strat(innings), data = bt2_cut , surv = TRUE , x=TRUE , y=TRUE , time.inc = 40)
validate(cox_ad_3,method = "randomization", u=40 ,B=40)
```