---
title: "LD_Chandimal"
author: "S/16/373_JAISHIEKA"
date: "12/13/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Loading the library**
```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(survival)
library(ggfortify)
library(survminer)
library(rms)
```
\
\
**Read the data set**
```{r, warning=FALSE,message=FALSE}
Home <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Home/Home.csv")
Overseas <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Overseas/Overseas.csv")
```
\
\
**Merge two data sets**
```{r, warning=FALSE,message=FALSE}
data_merge <- rbind(Home , Overseas)
```
\
\
**Filter the data of LD Chandimal**
```{r,warning=FALSE,message=FALSE}
bt1 <- data_merge %>% filter(grepl('LD Chandimal' , Striker))
head(bt1)
```
\
**Head of specific columns**
```{r,warning=FALSE,message=FALSE}
bt1 %>% select(innings,cum_balls,wicket,cum_runs,cum_singles,cum_doubles,cum_boundaries,cum_dotBalls) %>% head()
```
\
\
**Coxph model stratified for different innings**
```{r,warning=FALSE,message=FALSE}
cox_LD_1 <- coxph(Surv(cum_balls , wicket) ~ cum_runs+cum_singles+cum_doubles+cum_boundaries+cum_dotBalls + strata(innings), data = bt1)
summary(cox_LD_1)
```
\
**Interpreting the hazard ratios (exp(coef))**
\
\
**cum_runs(0.64959)** - There is a 35% of decrease in the hazard when the number of runs increased by 1 from the current ball to the next ball to be faced.
\
\
**cum_singles(0.11729)** - There is a 88% of decrease in the hazard when the number of singles scored is increased by 1 from the current ball to the next ball to be faced.
\
\
**cum_doubles(0.19978)** - There is a 80% of decrease in the hazard when the number of doubles scored is increased by 1 from the current ball to the next ball to be faced.
\
\
**cum_boundaries(0.46505)** - There is a 53% of decrease in the hazard when the number of boundaries scored is increased by 1 from the current ball to the next ball to be faced.
\
\
**cum_dotBalls(0.07632)** - There is a 92% of decrease in the hazard when the number of dot balls scored is increased by 1 from the current ball to the next ball to be faced.
\
\
We can see that the concordance is a high value and also the test statistics are statistically significant. Therefore we can say that this is a good model.
\
\
\
**Test for the proportional hazard assumptions**
```{r,warning=FALSE,message=FALSE}
test.ph.LD_1 <- cox.zph(cox_LD_1)
test.ph.LD_1
```
\
All the covariates and the global test are not statistically significant. Therefore we can say that the ph assumptions are not violated.
\
\
**Adjusted survival curve**
```{r,warning=FALSE,message=FALSE}
s1 <- ggadjustedcurves(cox_LD_1 , data = bt1 , size = 2,ggtheme = theme_survminer() , method = "average") + 
      geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") + 
      scale_x_continuous(breaks = seq(0,120,10)) + scale_y_continuous(breaks = seq(0,1,0.1))
s1
```
\
By the above graph we can see that Chandimal has a higher survival rate in the first and second innings for the first 20 balls. Then his survival rate is reducing. He has a 50% of survival rate when he is playing 30 to 40 balls in the first innings and playing around 35 balls in the second innings.
\
\
His survival probability is very low after 40th ball in the first innings and around 43rd ball in the second innings.
\
\
**Validating the model**
```{r,warning=FALSE,message=FALSE}
cox_ld <- cph(Surv(cum_balls , wicket) ~ cum_runs+cum_singles+cum_doubles+cum_boundaries+cum_dotBalls  + strat(innings), 
              data = bt1 , surv = TRUE , x=TRUE , y=TRUE , time.inc = 30)
validate(cox_ld, method = "randomization",u=30 ,B=40)
```