---
title: "AUC_BKG_INN"
author: "S_16_373"
date: "3/8/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Load the libraries**
```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(survival)
library(ggfortify)
library(survminer)
library(rms)
library(dynpred)
library(MASS)
library(CPE)
library(scatterplot3d)
library(plotly)
```
\
\
**Read the data sets**
```{r,warning=FALSE,message=FALSE}
Home <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Home/Home.csv")
Overseas <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Overseas/Overseas.csv")
```
\
\
**Merge two data sets**
```{r,warning=FALSE,message=FALSE}
data_merge <- rbind(Home , Overseas)
```
\
\
**Filter the data of BKG Mendis**
```{r,warning=FALSE,message=FALSE}
bt3 <- data_merge %>% filter(grepl('BKG Mendis' , Striker))
```
\
\
***1)Analysis for two different innings***
\
\
**First innings**
\
\
**Filter the first innings**
```{r,warning=FALSE,message=FALSE}
BKG_1 <- bt3 %>% filter(innings == 1)
```
\
\
**Cox model for first innings**
```{r,warning=FALSE,message=FALSE}
cox_BKG_1 <- coxph(Surv(cum_balls , wicket) ~ 
                     cum_runs+cum_singles+cum_doubles+cum_boundaries+ridge(cum_dotBalls), data = BKG_1)
summary(cox_BKG_1)
```
\
\
**Finding the best model using AIC**
```{r,warning=FALSE,message=FALSE}
model_BKG_1 <- stepAIC(cox_BKG_1)
```
\
\
**Best Model**
```{r,warning=FALSE,message=FALSE}
cox_BKG_1_new <- coxph(Surv(cum_balls , wicket) ~ 
                         cum_singles + cum_doubles + cum_boundaries+ ridge(cum_dotBalls), data = BKG_1)
summary(cox_BKG_1_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_BKG_1 <- cox.zph(cox_BKG_1_new)
test_BKG_1
```
\
\
**Extended cox model**
```{r,warning=FALSE,message=FALSE}
BKG_1_cut <- survSplit(BKG_1 , cut = 35 , end = "cum_balls" , event = "wicket" , start = "start" , id = "id")

BKG_1_cut$hv1 <- BKG_1_cut$cum_singles * (BKG_1_cut$start < 35)
BKG_1_cut$hv2 <- BKG_1_cut$cum_singles * (BKG_1_cut$start >= 35)


cox_BKG_1_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                     hv1 + hv2 +cum_doubles+ cum_boundaries+ridge(cum_dotBalls) + cluster (id) , data = BKG_1_cut)
summary(cox_BKG_1_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_BKG_1_heav <- cox.zph(cox_BKG_1_heav)
test_BKG_1_heav
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_BKG_1 <- ggadjustedcurves(cox_BKG_1_heav , data = BKG_1_cut , size = 2,ggtheme = theme_survminer()) + 
                  geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +xlim(0,70) +
                    ggtitle("Survival curve for BKG Mendis for the first innings") +
                    theme(text = element_text(size = 20))

cox_plot_BKG_1
```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE}
coef_plot_BKG_1 <- ggforest(cox_BKG_1_heav , data = BKG_1_cut,fontsize = 1.2)
coef_plot_BKG_1
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
                     hv1 + hv2 +cum_doubles+ cum_boundaries+ridge(cum_dotBalls) + cluster (id) , data = BKG_1_cut)
```
\
\
**percentage of matches won when the player is in the specific match**
```{r,warning=FALSE,message=FALSE}
match_status_BKG_1 <- unique(BKG_1[c("Match_Number","winning_status")])
tot_matches_BKG_1 <- nrow(match_status_BKG_1)
win_matches_BKG_1 <- sum(match_status_BKG_1$winning_status==1)

win_percent_BKG_1 <- (win_matches_BKG_1/tot_matches_BKG_1)*100

win_percent_BKG_1
```
\
\
**Runs contributed**
```{r,warning=FALSE,message=FALSE}
match_played_BKG_1 <- data_merge %>% filter(Match_Number %in% unique(BKG_1$Match_Number))
tot_runs_BKG_1 <- match_played_BKG_1 %>% summarise(sum_runs = sum(tot_runs))
BKG_runs_1 <- BKG_1 %>%  summarise(sum_runs = sum(tot_runs))

runs_contrib_percent_BKG_1 <- (BKG_runs_1/tot_runs_BKG_1)*100
runs_contrib_percent_BKG_1
```
\
\
**Second Innings**
\
\
**Filter the second innings**
```{r,warning=FALSE,message=FALSE}
BKG_2 <- bt3 %>% filter(innings == 2)
```
\
\
**Cox model for second innings**
```{r,warning=FALSE,message=FALSE}
cox_BKG_2 <- coxph(Surv(cum_balls , wicket) ~ 
                     cum_runs+cum_singles+cum_doubles+cum_boundaries+ridge(cum_dotBalls), data = BKG_2)
summary(cox_BKG_2)
```
\
\
**Finding the best model using AIC**
```{r,warning=FALSE,message=FALSE}
model_BKG_2 <- stepAIC(cox_BKG_2)
```
\
\
**Best Model**
```{r,warning=FALSE,message=FALSE}
cox_BKG_2_new <- coxph(Surv(cum_balls , wicket) ~ 
                          cum_singles + cum_boundaries+ ridge(cum_dotBalls), data = BKG_2)
summary(cox_BKG_2_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_BKG_2 <- cox.zph(cox_BKG_2_new)
test_BKG_2
```
\
\
**Extended cox model**
```{r,warning=FALSE,message=FALSE}
BKG_2_cut <- survSplit(BKG_2 , cut = 35 , end = "cum_balls" , event = "wicket" , start = "start" , id = "id")

BKG_2_cut$hv1 <- BKG_2_cut$cum_singles * (BKG_2_cut$start < 35)
BKG_2_cut$hv2 <- BKG_2_cut$cum_singles * (BKG_2_cut$start >= 35)


cox_BKG_2_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                     hv1 + hv2 +cum_boundaries+ridge(cum_dotBalls) + cluster (id) , data = BKG_2_cut)
summary(cox_BKG_2_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_BKG_2_heav <- cox.zph(cox_BKG_2_heav)
test_BKG_2_heav
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_BKG_2 <- ggadjustedcurves(cox_BKG_2_heav , data = BKG_2_cut , size = 2,ggtheme = theme_survminer()) + 
                  geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +
                    ggtitle("Survival curve for BKG Mendis for the second innings") +
                    theme(text = element_text(size = 20))

cox_plot_BKG_2
```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE}
coef_plot_BKG_2 <- ggforest(cox_BKG_2_heav , data = BKG_2_cut,fontsize = 1.2)
coef_plot_BKG_2
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
      hv1 + hv2 +cum_boundaries+ridge(cum_dotBalls) + cluster (id) , data = BKG_2_cut)
```
\
\
**percentage of matches won when the player is in the specific match**
```{r,warning=FALSE,message=FALSE}
match_status_BKG_2 <- unique(BKG_2[c("Match_Number","winning_status")])
tot_matches_BKG_2 <- nrow(match_status_BKG_2)
win_matches_BKG_2 <- sum(match_status_BKG_2$winning_status==1)

win_percent_BKG_2 <- (win_matches_BKG_2/tot_matches_BKG_2)*100

win_percent_BKG_2
```
\
\
**Runs contributed**
```{r,warning=FALSE,message=FALSE}
match_played_BKG_2 <- data_merge %>% filter(Match_Number %in% unique(BKG_2$Match_Number))
tot_runs_BKG_2 <- match_played_BKG_2 %>% summarise(sum_runs = sum(tot_runs))
BKG_runs_2 <- BKG_2 %>%  summarise(sum_runs = sum(tot_runs))

runs_contrib_percent_BKG_2 <- (BKG_runs_2/tot_runs_BKG_2)*100
runs_contrib_percent_BKG_2
```
\
\
\
***Compare different innings***
\
\
**Create the data frame**
```{r,warning=FALSE,message=FALSE}
PlayerName_BKG <- "BKG Mendis"
Innings <- c(1,2)
Survival_prob_BKG <- c(0.9685794,0.919333)
winning_percent_BKG <- c(37.77778,26.66667)
runs_contrib_percent_BKG <- c(14.01472,9.695122)

comp_innings_BKG <- data.frame(PlayerName_BKG,Innings,Survival_prob_BKG,runs_contrib_percent_BKG,winning_percent_BKG)
names(comp_innings_BKG) <- c("PlayerName","Innings","Survival_prob","runs_contrib_percent","winning_percent")
comp_innings_BKG
```
\
\
