---
title: "BKG_INN"
author: "S_16_373"
date: "5/8/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Load the libraries**
```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(survival)
library(ggfortify)
library(survminer)
library(rms)
library(dynpred)
library(MASS)
library(CPE)
library(scatterplot3d)
library(plotly)
```
\
\
**Read the data sets**
```{r,warning=FALSE,message=FALSE}
Home <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Home/Home.csv")
Overseas <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Overseas/Overseas.csv")
```
\
\
**Merge two data sets**
```{r,warning=FALSE,message=FALSE}
data_merge <- rbind(Home , Overseas)
```
\
\
**Filter the data of BKG Mendis**
```{r,warning=FALSE,message=FALSE}
bt3 <- data_merge %>% filter(grepl('BKG Mendis' , Striker))
```
\
\
***1)Analysis for two different innings***
\
\
```{r,message=FALSE,warning=FALSE}
BKG_diff_inn <- survdiff(Surv(cum_balls , wicket) ~ innings, data = bt3)
BKG_diff_inn
```
The p value is less than 0.05. Therefore there is a significant difference between the innings.

\
\
**First innings**
\
\
**Filter the first innings**
```{r,warning=FALSE,message=FALSE}
BKG_1 <- bt3 %>% filter(innings == 1)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
BKG_1_cut <- survSplit(BKG_1 , cut = 35 , end = "cum_balls" , event = "wicket" , start = "start" , id = "id")

BKG_1_cut$hv1 <- BKG_1_cut$cum_singles * (BKG_1_cut$start < 35)
BKG_1_cut$hv2 <- BKG_1_cut$cum_singles * (BKG_1_cut$start >= 35)


cox_BKG_1_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                          hv1 + hv2 + cum_boundaries+ridge(cum_dotBalls) + cluster (id) , data = BKG_1_cut)

summary(cox_BKG_1_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_BKG_1 <- cox.zph(cox_BKG_1_heav)
test_BKG_1
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_BKG_1 <- ggadjustedcurves(cox_BKG_1_heav , data = BKG_1_cut , size = 2,
                      ggtheme = theme_survminer()) + 
                      geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +
                      ggtitle("Survival curve for BKG Mendis for the first innings") + 
                      theme(axis.title = element_text(size = 15),
                            axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_BKG_1 <- ggforest(cox_BKG_1_heav , data = BKG_1_cut,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_BKG_1
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
                          hv1 + hv2 + cum_boundaries+ridge(cum_dotBalls) + cluster (id) , data = BKG_1_cut)
```
\
\
**Second Innings**
\
\
**Filter the second innings**
```{r,warning=FALSE,message=FALSE}
BKG_2 <- bt3 %>% filter(innings == 2)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
BKG_2_cut <- survSplit(BKG_2 , cut = 35 , end = "cum_balls" , event = "wicket" , start = "start" , id = "id")

BKG_2_cut$hv1 <- BKG_2_cut$cum_singles * (BKG_2_cut$start < 35)
BKG_2_cut$hv2 <- BKG_2_cut$cum_singles * (BKG_2_cut$start >= 35)


cox_BKG_2_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                          hv1 + hv2 +  cum_boundaries+ridge(cum_dotBalls) + cluster (id) , data = BKG_2_cut)
summary(cox_BKG_2_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_BKG_2 <- cox.zph(cox_BKG_2_heav)
test_BKG_2
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_BKG_2 <- ggadjustedcurves(cox_BKG_2_heav , data = BKG_2_cut , size = 2,
                        ggtheme = theme_survminer()) + 
                        geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +
                        ggtitle("Survival curve for BKG Mendis for the second innings") + 
                        theme(axis.title = element_text(size = 15),
                              axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_BKG_2 <- ggforest(cox_BKG_2_heav , data = BKG_2_cut,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_BKG_2
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
                          hv1 + hv2 +  cum_boundaries+ridge(cum_dotBalls) + cluster (id) , data = BKG_2_cut)
```
\
\
**Survival curve**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,6)}
BKGSurvPlotInn <- ggarrange(cox_plot_BKG_1,cox_plot_BKG_2,ncol = 2)
BKGSurvPlotInn
```
\
\
**Upload to texStudio**
```{r,results='hide',message=FALSE,warning=FALSE}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"BKGSurvPlotInn.eps"),width = 10,height = 7,horizontal = FALSE)
BKGSurvPlotInn
dev.off()
```
\
\
**Aalen model**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,7)}
BKG_1_cut <- rename(BKG_1_cut,cumulative_singles_lt35 = hv1, cumulative_singles_ge35 = hv2 ,cumulative_fours = 
                    cum_boundaries,cumulative_dot_balls=cum_dotBalls)
BKG_2_cut <- rename(BKG_2_cut,cumulative_singles_lt35 = hv1, cumulative_singles_ge35 = hv2,cumulative_fours = 
                    cum_boundaries,cumulative_dot_balls=cum_dotBalls)

BKG_p1 <- autoplot(aareg(Surv(start,cum_balls , wicket) ~ 
                          cumulative_singles_lt35 + cumulative_singles_ge35 +  cumulative_fours+ridge(cumulative_dot_balls) + 
                           cluster (id) , data = BKG_1_cut)) + theme(legend.position = "none") + 
  ggtitle("Aalen plot of BKG Mendis for the first innings") 

BKG_p2 <- autoplot(aareg(Surv(start,cum_balls , wicket) ~ 
                          cumulative_singles_lt35 + cumulative_singles_ge35 +  cumulative_fours+ridge(cumulative_dot_balls) + 
                           cluster (id) , data = BKG_2_cut)) + theme(legend.position = "none") + 
  ggtitle("Aalen plot of BKG Mendis for the second innings") 

BKGAalenInn <- ggarrange(BKG_p1,BKG_p2, nrow = 2)
BKGAalenInn
```

```{r,warning=FALSE,message=FALSE,results='hide'}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"BKGAalenInn.eps"),width = 10,height = 7,horizontal = FALSE)
BKGAalenInn
dev.off()
```