---
title: "BKG_VEN"
author: "S_16_373"
date: "5/8/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Load the libraries**
```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(survival)
library(ggfortify)
library(survminer)
library(rms)
library(dynpred)
library(MASS)
library(CPE)
library(scatterplot3d)
library(plotly)
```
\
\
**Read the data sets**
```{r,warning=FALSE,message=FALSE}
Home <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Home/Home.csv")
Overseas <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Overseas/Overseas.csv")
```
\
\
**Merge two data sets**
```{r,warning=FALSE,message=FALSE}
data_merge <- rbind(Home , Overseas)
```
\
\
**Filter the data of BKG Mendis**
```{r,warning=FALSE,message=FALSE}
bt3 <- data_merge %>% filter(grepl('BKG Mendis' , Striker))
```
\
\
***1)Analysis for two different Venue***
\
\
```{r,message=FALSE,warning=FALSE}
BKG_diff_ven <- survdiff(Surv(cum_balls , wicket) ~ Venue, data = bt3)
BKG_diff_ven
```
The p value is less than 0.05. Therefore there is a significant difference between the Venue.

\
\
**Home**
\
\
**Filter the first Venue**
```{r,warning=FALSE,message=FALSE}
BKG_H <- bt3 %>% filter(Venue == "Home")
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
BKG_H_cut <- survSplit(BKG_H , cut = 30 , end = "cum_balls" , event = "wicket" , start = "start" , id = "id")

BKG_H_cut$hv1 <- BKG_H_cut$cum_singles * (BKG_H_cut$start < 30)
BKG_H_cut$hv2 <- BKG_H_cut$cum_singles * (BKG_H_cut$start >= 30)


cox_BKG_H_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                          hv1 + hv2 +cum_doubles+ cum_boundaries+ridge(cum_dotBalls) + cluster (id) , 
                        data = BKG_H_cut)

summary(cox_BKG_H_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_BKG_H <- cox.zph(cox_BKG_H_heav)
test_BKG_H
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_BKG_H <- ggadjustedcurves(cox_BKG_H_heav , data = BKG_H_cut , size = 2,
                          ggtheme = theme_survminer()) + 
                          geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +
                          ggtitle("Survival curve for BKG Mendis for Venue Home") + 
                          theme(axis.title = element_text(size = 15),
                                axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_BKG_H <- ggforest(cox_BKG_H_heav , data = BKG_H_cut,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_BKG_H
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
                          hv1 + hv2 +cum_doubles+ cum_boundaries+ridge(cum_dotBalls) + cluster (id) , 
                        data = BKG_H_cut)
```
\
\
**Second Venue**
\
\
**Filter the second Venue**
```{r,warning=FALSE,message=FALSE}
BKG_O <- bt3 %>% filter(Venue == "Overseas")
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
BKG_O_cut <- survSplit(BKG_O , cut = 30 , end = "cum_balls" , event = "wicket" , start = "start" , id = "id")

BKG_O_cut$hv1 <- BKG_O_cut$cum_singles * (BKG_O_cut$start < 30)
BKG_O_cut$hv2 <- BKG_O_cut$cum_singles * (BKG_O_cut$start >= 30)


cox_BKG_O_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                          hv1 + hv2 +cum_doubles+ cum_boundaries+ridge(cum_dotBalls) + cluster (id) ,
                        data = BKG_O_cut)
summary(cox_BKG_O_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_BKG_O <- cox.zph(cox_BKG_O_heav)
test_BKG_O
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_BKG_O <- ggadjustedcurves(cox_BKG_O_heav , data = BKG_O_cut , size = 2,
                          ggtheme = theme_survminer()) + 
                          geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +
                          ggtitle("Survival curve for BKG Mendis for Venue Overseas") + 
                          theme(axis.title = element_text(size = 15),
                                axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_BKG_O <- ggforest(cox_BKG_O_heav , data = BKG_O_cut,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_BKG_O
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
                          hv1 + hv2 +cum_doubles+ cum_boundaries+ridge(cum_dotBalls) + cluster (id) ,
                        data = BKG_O_cut)
```
\
\
**Survival curve**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,6)}
BKGSurvPlotVen <- ggarrange(cox_plot_BKG_H,cox_plot_BKG_O,ncol = 2)
BKGSurvPlotVen
```
\
\
**Upload to texStudio**
```{r,results='hide',message=FALSE,warning=FALSE}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"BKGSurvPlotVen.eps"),width = 10,height = 7,horizontal = FALSE)
BKGSurvPlotVen
dev.off()
```
\
\
**Aalen model**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,7)}
BKG_H_cut <- rename(BKG_H_cut,cumulative_singles_lt30 = hv1, cumulative_singles_ge30 = hv2 ,cumulative_doubles = 
                      cum_doubles,cumulative_fours = cum_boundaries,cumulative_dot_balls=cum_dotBalls)
BKG_O_cut <- rename(BKG_O_cut,cumulative_singles_lt30 = hv1, cumulative_singles_ge30 = hv2,cumulative_doubles = 
                      cum_doubles,cumulative_fours = cum_boundaries,cumulative_dot_balls=cum_dotBalls)

BKG_pH <- autoplot(aareg(Surv(start,cum_balls , wicket) ~ 
                          cumulative_singles_lt30 + cumulative_singles_ge30 +cumulative_doubles+ 
                           cumulative_fours+ridge(cumulative_dot_balls) + cluster (id) ,data = BKG_H_cut)) +
  theme(legend.position = "none") + ggtitle("Aalen plot of BKG Mendis for home venue")

BKG_pO <- autoplot(aareg(Surv(start,cum_balls , wicket) ~ 
                          cumulative_singles_lt30 + cumulative_singles_ge30 +cumulative_doubles+ 
                           cumulative_fours+ridge(cumulative_dot_balls) + cluster (id) ,data = BKG_O_cut)) +
  theme(legend.position = "none") + ggtitle("Aalen plot of BKG Mendis for overseas venue")

BKGAalenVen <- ggarrange(BKG_pH,BKG_pO, nrow = 2)
BKGAalenVen
```

```{r,warning=FALSE,message=FALSE,results='hide'}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"BKGAalenVen.eps"),width = 10,height = 7,horizontal = FALSE)
BKGAalenVen
dev.off()
```