---
title: "DMS"
author: "S_16_373"
date: "3/9/2022"
output: pdf_document
---

**Load the libraries**
```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(survival)
library(ggfortify)
library(survminer)
library(rms)
library(dynpred)
library(MASS)
library(CPE)
library(scatterplot3d)
library(plotly)
```
\
\
**Read the data sets**
```{r,warning=FALSE,message=FALSE}
Home <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Home/Home.csv")
Overseas <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Overseas/Overseas.csv")
```
\
\
**Merge two data sets**
```{r,warning=FALSE,message=FALSE}
data_merge <- rbind(Home , Overseas)
```
\
\
**Filter the data of DM de Silva**
```{r,warning=FALSE,message=FALSE}
bt <- data_merge %>% filter(grepl('DM de Silva' , Striker))
```
\
\
***1)Analysis for two different innings***
\
\
**First innings**
\
\
**Filter the first innings**
```{r,warning=FALSE,message=FALSE}
DMS_1 <- bt %>% filter(innings == 1)
```
\
\
**Cox model for first innings**
```{r,warning=FALSE,message=FALSE}
cox_DMS_1 <- coxph(Surv(cum_balls , wicket) ~ 
                     cum_runs+cum_singles+cum_doubles+cum_boundaries+ridge(cum_dotBalls), data = DMS_1)
summary(cox_DMS_1)
```
\
\
**Finding the best model using AIC**
```{r,warning=FALSE,message=FALSE}
model_DMS_1 <- stepAIC(cox_DMS_1)
```
\
\
**Best Model**
```{r,warning=FALSE,message=FALSE}
cox_DMS_1_new <- coxph(Surv(cum_balls , wicket) ~ 
                         cum_singles +  cum_boundaries+ ridge(cum_dotBalls), data = DMS_1)
summary(cox_DMS_1_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_DMS_1 <- cox.zph(cox_DMS_1_new)
test_DMS_1
```
\
\
**Extended cox model**
```{r,warning=FALSE,message=FALSE}
DMS_1_cut <- survSplit(DMS_1 , cut = 27 , end = "cum_balls" , event = "wicket" , start = "start" , id = "id")

DMS_1_cut$hv1 <- DMS_1_cut$cum_boundaries  * (DMS_1_cut$start < 27)
DMS_1_cut$hv2 <- DMS_1_cut$cum_boundaries  * (DMS_1_cut$start >= 27)

cox_DMS_1_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                     cum_singles +hv1 + hv2 + ridge(cum_dotBalls) + cluster (id) , data = DMS_1_cut)
summary(cox_DMS_1_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_DMS_1_heav <- cox.zph(cox_DMS_1_heav)
test_DMS_1_heav
```
\
\
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_DMS_1 <- ggadjustedcurves(cox_DMS_1_heav , data = DMS_1_cut , size = 2,ggtheme = theme_survminer()) + 
                  geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +
                    ggtitle("Survival curve for DM de Silva for the first innings") +
                    theme(text = element_text(size = 20))

cox_plot_DMS_1
```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE}
coef_plot_DMS_1 <- ggforest(cox_DMS_1_heav , data = DMS_1_cut,fontsize = 1.2)
coef_plot_DMS_1
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
      cum_singles +hv1 + hv2 + ridge(cum_dotBalls) + cluster (id) , data = DMS_1_cut)
```
\
\
**percentage of matches won when the player is in the specific match**
```{r,warning=FALSE,message=FALSE}
match_status_DMS_1 <- unique(DMS_1[c("Match_Number","winning_status")])
tot_matches_DMS_1 <- nrow(match_status_DMS_1)
win_matches_DMS_1 <- sum(match_status_DMS_1$winning_status==1)

win_percent_DMS_1 <- (win_matches_DMS_1/tot_matches_DMS_1)*100

win_percent_DMS_1
```
\
\
**Runs contributed**
```{r,warning=FALSE,message=FALSE}
match_played_DMS_1 <- data_merge %>% filter(Match_Number %in% unique(DMS_1$Match_Number))
tot_runs_DMS_1 <- match_played_DMS_1 %>% summarise(sum_runs = sum(tot_runs))
DMS_runs_1 <- DMS_1 %>%  summarise(sum_runs = sum(tot_runs))

runs_contrib_percent_DMS_1 <- (DMS_runs_1/tot_runs_DMS_1)*100
runs_contrib_percent_DMS_1
```
\
\
**Second Innings**
\
\
**Filter the second innings**
```{r,warning=FALSE,message=FALSE}
DMS_2 <- bt %>% filter(innings == 2)
```
\
\
**Cox model for second innings**
```{r,warning=FALSE,message=FALSE}
cox_DMS_2 <- coxph(Surv(cum_balls , wicket) ~ 
                     cum_runs+cum_singles+cum_doubles+cum_boundaries+ridge(cum_dotBalls), data = DMS_2)
summary(cox_DMS_2)
```
\
\
**Finding the best model using AIC**
```{r,warning=FALSE,message=FALSE}
model_DMS_2 <- stepAIC(cox_DMS_2)
```
\
\
**Best Model**
```{r,warning=FALSE,message=FALSE}
cox_DMS_2_new <- coxph(Surv(cum_balls , wicket) ~ 
                          cum_singles + cum_boundaries+ ridge(cum_dotBalls), data = DMS_2)
summary(cox_DMS_2_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_DMS_2 <- cox.zph(cox_DMS_2_new)
test_DMS_2
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_DMS_2 <- ggadjustedcurves(cox_DMS_2_new , data = DMS_2 , size = 2,ggtheme = theme_survminer()) + 
                  geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +
                    ggtitle("Survival curve for DM de Silva for the second innings") +
                    theme(text = element_text(size = 20))

cox_plot_DMS_2
```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE}
coef_plot_DMS_2 <- ggforest(cox_DMS_2_new , data = DMS_2,fontsize = 1.2)
coef_plot_DMS_2
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(cum_balls , wicket) ~ 
      cum_singles + cum_doubles + cum_boundaries+ ridge(cum_dotBalls), data = DMS_2)
```
\
\
**percentage of matches won when the player is in the specific match**
```{r,warning=FALSE,message=FALSE}
match_status_DMS_2 <- unique(DMS_2[c("Match_Number","winning_status")])
tot_matches_DMS_2 <- nrow(match_status_DMS_2)
win_matches_DMS_2 <- sum(match_status_DMS_2$winning_status==1)

win_percent_DMS_2 <- (win_matches_DMS_2/tot_matches_DMS_2)*100

win_percent_DMS_2
```
\
\
**Runs contributed**
```{r,warning=FALSE,message=FALSE}
match_played_DMS_2 <- data_merge %>% filter(Match_Number %in% unique(DMS_2$Match_Number))
tot_runs_DMS_2 <- match_played_DMS_2 %>% summarise(sum_runs = sum(tot_runs))
DMS_runs_2 <- DMS_2 %>%  summarise(sum_runs = sum(tot_runs))

runs_contrib_percent_DMS_2 <- (DMS_runs_2/tot_runs_DMS_2)*100
runs_contrib_percent_DMS_2
```
\
\
\
***Compare different innings***
\
\
**Create the data frame**
```{r,warning=FALSE,message=FALSE}
PlayerName_DMS <- "DM de Silva"
Innings <- c(1,2)
Survival_prob_DMS <- c(0.9606935,0.946015)
winning_percent_DMS <- c(43.33333,18.75)
runs_contrib_percent_DMS <- c(10.16244	,11.12124)

comp_innings_DMS <- data.frame(PlayerName_DMS,Innings,Survival_prob_DMS,runs_contrib_percent_DMS,winning_percent_DMS)
names(comp_innings_DMS) <- c("PlayerName","Innings","Survival_prob","runs_contrib_percent","winning_percent")
comp_innings_DMS
```
\
\
