---
title: "DMS_VEN"
author: "S_16_373"
date: "5/8/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Load the libraries**
```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(survival)
library(ggfortify)
library(survminer)
library(rms)
library(dynpred)
library(MASS)
library(CPE)
library(scatterplot3d)
library(plotly)
```
\
\
**Read the data sets**
```{r,warning=FALSE,message=FALSE}
Home <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Home/Home.csv")
Overseas <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Overseas/Overseas.csv")
```
\
\
**Merge two data sets**
```{r,warning=FALSE,message=FALSE}
data_merge <- rbind(Home , Overseas)
```
\
\
**Filter the data of DM de Silva**
```{r,warning=FALSE,message=FALSE}
bt <- data_merge %>% filter(grepl('DM de Silva' , Striker))
```
\
\
***1)Analysis for two different Venue***
\
\
```{r,message=FALSE,warning=FALSE}
DMS_diff_ven <- survdiff(Surv(cum_balls , wicket) ~ Venue, data = bt)
DMS_diff_ven
```
The p value is greater than 0.05. Therefore we cannot see a significant difference between the Venue.

\
\
**Home**
\
\
**Filter the first Venue**
```{r,warning=FALSE,message=FALSE}
DMS_H <- bt %>% filter(Venue == "Home")
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
DMS_H_cut <- survSplit(DMS_H , cut = 30 , end = "cum_balls" , event = "wicket" , start = "start" , id = "id")

DMS_H_cut$hv1 <- DMS_H_cut$cum_singles  * (DMS_H_cut$start < 30)
DMS_H_cut$hv2 <- DMS_H_cut$cum_singles  * (DMS_H_cut$start >= 30)

cox_DMS_H_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                          hv1 + hv2 + cum_boundaries+ ridge(cum_dotBalls) + cluster (id) , data = DMS_H_cut)

summary(cox_DMS_H_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_DMS_H <- cox.zph(cox_DMS_H_heav)
test_DMS_H
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_DMS_H <- ggadjustedcurves(cox_DMS_H_heav , data = DMS_H_cut , size = 2,
                          ggtheme = theme_survminer()) + 
                          geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +
                          ggtitle("Survival curve for DM de Silva for Venue Home") + 
                          theme(axis.title = element_text(size = 15),
                                axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_DMS_H <- ggforest(cox_DMS_H_heav , data = DMS_H_cut,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_DMS_H
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
                          hv1 + hv2 + cum_boundaries+ ridge(cum_dotBalls) + cluster (id) , data = DMS_H_cut)
```
\
\
**Second Venue**
\
\
**Filter the second Venue**
```{r,warning=FALSE,message=FALSE}
DMS_O <- bt %>% filter(Venue == "Overseas")
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
DMS_O_cut <- survSplit(DMS_O , cut = 30 , end = "cum_balls" , event = "wicket" , start = "start" , id = "id")

DMS_O_cut$hv1 <- DMS_O_cut$cum_singles  * (DMS_O_cut$start < 30)
DMS_O_cut$hv2 <- DMS_O_cut$cum_singles  * (DMS_O_cut$start >= 30)

cox_DMS_O_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                          hv1 + hv2 + cum_boundaries+ ridge(cum_dotBalls) + cluster (id) , data = DMS_O_cut)
summary(cox_DMS_O_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_DMS_O <- cox.zph(cox_DMS_O_heav)
test_DMS_O
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_DMS_O <- ggadjustedcurves(cox_DMS_O_heav , data = DMS_O_cut , size = 2,
                          ggtheme = theme_survminer()) + 
                          geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +
                          ggtitle("Survival curve for DM de Silva for Venue Overseas") + 
                          theme(axis.title = element_text(size = 15),
                                axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_DMS_O <- ggforest(cox_DMS_O_heav , data = DMS_O_cut,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_DMS_O
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
                          hv1 + hv2 + cum_boundaries+ ridge(cum_dotBalls) + cluster (id) , data = DMS_O_cut)
```
\
\
**Survival curve**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,6)}
DMSSurvPlotVen <- ggarrange(cox_plot_DMS_H,cox_plot_DMS_O,ncol = 2)
DMSSurvPlotVen
```
\
\
**Upload to texStudio**
```{r,results='hide',message=FALSE,warning=FALSE}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"DMSSurvPlotVen.eps"),width = 10,height = 7,horizontal = FALSE)
DMSSurvPlotVen
dev.off()
```
\
\
**Aalen model**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,7)}
DMS_H_cut <- rename(DMS_H_cut,cumulative_singles_lt30 = hv1, cumulative_singles_ge30 = 
                      hv2,cumulative_fours = cum_boundaries,cumulative_dot_balls=cum_dotBalls)
DMS_O_cut <- rename(DMS_O_cut,cumulative_singles_lt30 = hv1, cumulative_singles_ge30 = 
                      hv2,cumulative_fours = cum_boundaries,cumulative_dot_balls=cum_dotBalls)

DMS_pH <- autoplot(aareg(Surv(start,cum_balls , wicket) ~ 
                          cumulative_singles_lt30 + cumulative_singles_ge30 + cumulative_fours+ ridge(cumulative_dot_balls) + 
                           cluster (id) , data = DMS_H_cut))+theme(legend.position = "none") + 
  ggtitle("Aalen plot of DM de Silva for home venue")

DMS_pO <- autoplot(aareg(Surv(start,cum_balls , wicket) ~ 
                          cumulative_singles_lt30 + cumulative_singles_ge30 + cumulative_fours+ ridge(cumulative_dot_balls) + 
                           cluster (id) , data = DMS_O_cut))+ theme(legend.position = "none") + 
  ggtitle("Aalen plot of DM de Silva for overseas venue")

DMSAalenVen <- ggarrange(DMS_pH,DMS_pO, nrow = 2)
DMSAalenVen
```

```{r,warning=FALSE,message=FALSE,results='hide'}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"DMSAalenVen.eps"),width = 10,height = 7,horizontal = FALSE)
DMSAalenVen
dev.off()
```