---
title: "DMS_POS"
author: "S_16_373"
date: "5/8/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
**Load the libraries**
```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(survival)
library(ggfortify)
library(survminer)
library(rms)
library(dynpred)
library(MASS)
library(CPE)
library(scatterplot3d)
library(plotly)
```
\
\
**Read the data sets**
```{r,warning=FALSE,message=FALSE}
Home <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Home/Home.csv")
Overseas <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Overseas/Overseas.csv")
```
\
\
**Merge two data sets**
```{r,warning=FALSE,message=FALSE}
data_merge <- rbind(Home , Overseas)
```
\
\
**Filter the data of DM de Silva**
```{r,warning=FALSE,message=FALSE}
bt <- data_merge %>% filter(grepl('DM de Silva' , Striker))
```
\
\
***1)Analysis for different batting position***
\
\
```{r,message=FALSE,warning=FALSE}
bt_ps <- bt %>% filter(bat_position == c(5,6,7))

DMS_diff_pos <- survdiff(Surv(cum_balls , wicket) ~ bat_position, data = bt_ps)
DMS_diff_pos
```
The p value is greater than 0.05. Therefore we cannot see a significant difference between the batting positions 5,6 and 7.
\
\
**batting position 5**
\
\
**Filter the first bat_position**
```{r,warning=FALSE,message=FALSE}
DMS_P_5<- bt %>% filter(bat_position == 5)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
DMS_P_5_cut <- survSplit(DMS_P_5 , cut = 30 , end = "cum_balls" , event = "wicket" , start = "start" , id = "id")

DMS_P_5_cut$hv1 <- DMS_P_5_cut$cum_runs  * (DMS_P_5_cut$start < 30)
DMS_P_5_cut$hv2 <- DMS_P_5_cut$cum_runs  * (DMS_P_5_cut$start >= 30)

cox_DMS_P_5_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                            cum_singles +hv1 + hv2 + cum_boundaries + ridge(cum_dotBalls) + cluster (id) , 
                          data = DMS_P_5_cut)

summary(cox_DMS_P_5_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_DMS_P_5 <- cox.zph(cox_DMS_P_5_heav)
test_DMS_P_5
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_DMS_P_5 <- ggadjustedcurves(cox_DMS_P_5_heav , data = DMS_P_5_cut , size = 2,
                        ggtheme =theme_survminer()) + geom_hline(yintercept = c(0.25,0.5,0.75) ,
                        linetype = "dashed") +ggtitle("Survival curve for DM de Silva for the 5th
                        batting position") + theme(axis.title = element_text(size = 15),axis.text = 
                        element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_DMS_P_5 <- ggforest(cox_DMS_P_5_heav , data = DMS_P_5_cut,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_DMS_P_5
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
      cum_singles +hv1 + hv2 + cum_boundaries + ridge(cum_dotBalls) + cluster (id) , data = DMS_P_5_cut)
```
\
\
**batting position 6**
\
\
**Filter the first bat_position**
```{r,warning=FALSE,message=FALSE }
DMS_P_6<- bt %>% filter(bat_position == 6)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
DMS_P_6_cut <- survSplit(DMS_P_6 , cut = 30 , end = "cum_balls" , event = "wicket" , start = "start" , id = "id")

DMS_P_6_cut$hv1 <- DMS_P_6_cut$cum_runs  * (DMS_P_6_cut$start < 30)
DMS_P_6_cut$hv2 <- DMS_P_6_cut$cum_runs  * (DMS_P_6_cut$start >= 30)

cox_DMS_P_6_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                            cum_singles +hv1 + hv2 + cum_boundaries + ridge(cum_dotBalls) + cluster (id) , 
                          data = DMS_P_6_cut)

summary(cox_DMS_P_6_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_DMS_P_6 <- cox.zph(cox_DMS_P_6_heav)
test_DMS_P_6
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_DMS_P_6 <- ggadjustedcurves(cox_DMS_P_6_heav , data = DMS_P_6_cut , size = 2,
                        ggtheme =theme_survminer()) + geom_hline(yintercept = c(0.25,0.5,0.75) ,
                        linetype = "dashed") +ggtitle("Survival curve for DM de Silva for the 6th
                        batting position") + theme(axis.title = element_text(size = 15),axis.text = 
                        element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_DMS_P_6 <- ggforest(cox_DMS_P_6_heav , data = DMS_P_6_cut,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_DMS_P_6
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
      cum_singles +hv1 + hv2 + cum_boundaries + ridge(cum_dotBalls) + cluster (id) , data = DMS_P_6_cut)
```
\
\
\
\
**7th batting position**
\
\
**Filter the second bat_position**
```{r,warning=FALSE,message=FALSE}
DMS_P_7 <- bt %>% filter(bat_position == 7)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
DMS_P_7_cut <- survSplit(DMS_P_7 , cut = 30 , end = "cum_balls" , event = "wicket" , start = "start" , id = "id")

DMS_P_7_cut$hv1 <- DMS_P_7_cut$cum_runs  * (DMS_P_7_cut$start < 30)
DMS_P_7_cut$hv2 <- DMS_P_7_cut$cum_runs  * (DMS_P_7_cut$start >= 30)

cox_DMS_P_7_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                            cum_singles +hv1 + hv2 + cum_boundaries + ridge(cum_dotBalls) + cluster (id) , 
                          data = DMS_P_7_cut)
summary(cox_DMS_P_7_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_DMS_P_7 <- cox.zph(cox_DMS_P_7_heav)
test_DMS_P_7
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_DMS_P_7 <- ggadjustedcurves(cox_DMS_P_7_heav , data = DMS_P_7_cut , size = 2,ggtheme = 
                        theme_survminer()) + geom_hline(yintercept = c(0.25,0.5,0.75) , 
                        linetype = "dashed") +ggtitle("Survival curve for DM de Silva for 
                        the 7th batting position") + theme(axis.title = element_text(size = 15),
                        axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_DMS_P_7 <- ggforest(cox_DMS_P_7_heav , data = DMS_P_7_cut,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_DMS_P_7
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
      cum_singles +hv1 + hv2 + cum_boundaries + ridge(cum_dotBalls) + cluster (id) , data = DMS_P_7_cut)
```
\
\
**Survival curve**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,6)}
DMSSurvPlotPos <- ggarrange(cox_plot_DMS_P_5,cox_plot_DMS_P_6,cox_plot_DMS_P_7)
DMSSurvPlotPos
```
\
\
**Upload to texStudio**
```{r,results='hide',message=FALSE,warning=FALSE}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"DMSSurvPlotPos.eps"),width = 10,height = 7,horizontal = FALSE)
DMSSurvPlotPos
dev.off()
```
\
\
**Aalen model**
```{r,warning=FALSE,message=FALSE,fig.dim=c(15,20)}
DMS_P_5_cut <- rename(DMS_P_5_cut,cumulative_singles = cum_singles,cumulative_runs_lt30 = hv1, cumulative_runs_ge30 = 
                      hv2,cumulative_fours = cum_boundaries,cumulative_dot_balls=cum_dotBalls)
DMS_P_6_cut <- rename(DMS_P_6_cut,cumulative_singles = cum_singles,cumulative_runs_lt30 = hv1, cumulative_runs_ge30 = 
                      hv2,cumulative_fours = cum_boundaries,cumulative_dot_balls=cum_dotBalls)
DMS_P_7_cut <- rename(DMS_P_7_cut,cumulative_singles = cum_singles,cumulative_runs_lt30 = hv1, cumulative_runs_ge30 = 
                      hv2,cumulative_fours = cum_boundaries,cumulative_dot_balls=cum_dotBalls)


DMS_p5 <- autoplot(aareg(Surv(start,cum_balls , wicket) ~ 
      cumulative_singles +cumulative_runs_lt30 + cumulative_runs_ge30 + cumulative_fours + ridge(cumulative_dot_balls) + 
        cluster (id) , data = DMS_P_5_cut)) +theme(legend.position = "none") + 
  ggtitle("Aalen plot of DM de Silva for 5th batting position")

DMS_p6 <- autoplot(aareg(Surv(start,cum_balls , wicket) ~ 
      cumulative_singles +cumulative_runs_lt30 + cumulative_runs_ge30 + cumulative_fours + ridge(cumulative_dot_balls) + 
        cluster (id) , data = DMS_P_6_cut)) +theme(legend.position = "none") + 
  ggtitle("Aalen plot of DM de Silva for 6th batting position")

DMS_p7 <- autoplot(aareg(Surv(start,cum_balls , wicket) ~ 
      cumulative_singles +cumulative_runs_lt30 + cumulative_runs_ge30 + cumulative_fours + ridge(cumulative_dot_balls) + 
        cluster (id) , data = DMS_P_7_cut)) +theme(legend.position = "none") + 
  ggtitle("Aalen plot of DM de Silva for 7th batting position")

DMSAalenPos <- ggarrange(DMS_p5,DMS_p6,DMS_p7, nrow = 3)
DMSAalenPos
```

```{r,warning=FALSE,message=FALSE,results='hide'}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"DMSAalenPos.eps"),width = 10,height = 20,horizontal = FALSE)
DMSAalenPos
dev.off()
```