---
title: "NLTC_POS"
author: "S_16_373"
date: "4/25/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Load the libraries**
```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(survival)
library(ggfortify)
library(survminer)
library(rms)
library(dynpred)
library(MASS)
library(CPE)
library(scatterplot3d)
library(plotly)
```
\
\
**Read the data sets**
```{r,warning=FALSE,message=FALSE}
Home <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Home/Home.csv")
Overseas <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Overseas/Overseas.csv")
```
\
\
**Merge two data sets**
```{r,warning=FALSE,message=FALSE}
data_merge <- rbind(Home , Overseas)
```
\
\
**Filter the data of NLTC Perera**
```{r,warning=FALSE,message=FALSE}
bt12 <- data_merge %>% filter(grepl('NLTC Perera' , Striker))
```
\
\
***1)Analysis for different batting position***
\
\
```{r,message=FALSE,warning=FALSE}
bt12_ps <- bt12 %>% filter(bat_position == c(7,8))

NLTC_diff_pos <- survdiff(Surv(cum_balls , wicket) ~ bat_position, data = bt12_ps)
NLTC_diff_pos
```
The p value is less than 0.05. Therefore there is a significant difference between the batting positions 7 and 8.

\
\
**batting position 7**
\
\
**Filter the first bat_position**
```{r,warning=FALSE,message=FALSE}
NLTC_P_7<- bt12 %>% filter(bat_position == 7)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
NLTC_P_7_cut <- survSplit(NLTC_P_7 , cut = 20 , end = "cum_balls" , event = "wicket" , 
                          start = "start" , id = "id")

NLTC_P_7_cut$hv1 <- NLTC_P_7_cut$cum_runs * (NLTC_P_7_cut$start < 20)
NLTC_P_7_cut$hv2 <- NLTC_P_7_cut$cum_runs * (NLTC_P_7_cut$start >= 20)


cox_NLTC_P_7_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                             hv1 +hv2 + cum_boundaries  + ridge(cum_dotBalls) + 
                             cluster (id) , data = NLTC_P_7_cut)

summary(cox_NLTC_P_7_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_NLTC_P_7 <- cox.zph(cox_NLTC_P_7_heav)
test_NLTC_P_7
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_NLTC_P_7 <- ggadjustedcurves(cox_NLTC_P_7_heav , data = NLTC_P_7_cut , size = 2,
                        ggtheme =theme_survminer()) + geom_hline(yintercept = c(0.25,0.5,0.75) ,
                        linetype = "dashed") +ggtitle("Survival curve for NLTC Perera for the 7th
                        batting position") + theme(axis.title = element_text(size = 15),axis.text = 
                        element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_NLTC_P_7 <- ggforest(cox_NLTC_P_7_heav , data = NLTC_P_7_cut,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_NLTC_P_7
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
      hv1 +hv2 + cum_boundaries  + ridge(cum_dotBalls) + cluster (id) , data = NLTC_P_7_cut)
```
\
\
**8th batting position**
\
\
**Filter the second bat_position**
```{r,warning=FALSE,message=FALSE}
NLTC_P_8 <- bt12 %>% filter(bat_position == 8)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
NLTC_P_8_cut <- survSplit(NLTC_P_8 , cut = 20 , end = "cum_balls" , event = "wicket" , 
                          start = "start" , id = "id")

NLTC_P_8_cut$hv1 <- NLTC_P_8_cut$cum_runs * (NLTC_P_8_cut$start < 20)
NLTC_P_8_cut$hv2 <- NLTC_P_8_cut$cum_runs * (NLTC_P_8_cut$start >= 20)


cox_NLTC_P_8_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                           hv1 + hv2 +  cum_boundaries + ridge(cum_dotBalls) + cluster (id) , 
                           data = NLTC_P_8_cut)
summary(cox_NLTC_P_8_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_NLTC_P_8 <- cox.zph(cox_NLTC_P_8_heav)
test_NLTC_P_8
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_NLTC_P_8 <- ggadjustedcurves(cox_NLTC_P_8_heav , data = NLTC_P_8_cut , size = 2,ggtheme = 
                        theme_survminer()) + geom_hline(yintercept = c(0.25,0.5,0.75) , 
                        linetype = "dashed") +ggtitle("Survival curve for NLTC Perera for 
                        the 8th batting position") + theme(axis.title = element_text(size = 15),
                        axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_NLTC_P_8 <- ggforest(cox_NLTC_P_8_heav , data = NLTC_P_8_cut,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_NLTC_P_8
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
      hv1 + hv2 +  cum_boundaries + ridge(cum_dotBalls) + cluster (id) , data = NLTC_P_8_cut)
```
\
\
**Survival curve**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,6)}
NLTCSurvPlotPos <- ggarrange(cox_plot_NLTC_P_7,cox_plot_NLTC_P_8,ncol = 2)
NLTCSurvPlotPos
```
\
\
**Upload to texStudio**
```{r,results='hide',message=FALSE,warning=FALSE}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"NLTCSurvPlotPos.eps"),width = 10,height = 7,horizontal = FALSE)
NLTCSurvPlotPos
dev.off()
```
\
\
**Aalen model**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,7)}
NLTC_P_7_cut <- rename(NLTC_P_7_cut,cumulative_runs_lt20 = hv1, cumulative_runs_ge20 = hv2 ,cumulative_fours = 
                    cum_boundaries,cumulative_dot_balls=cum_dotBalls)
NLTC_P_8_cut <- rename(NLTC_P_8_cut,cumulative_runs_lt20 = hv1, cumulative_runs_ge20 = hv2 ,cumulative_fours = 
                    cum_boundaries,cumulative_dot_balls=cum_dotBalls)

NLTC_p7 <- autoplot(aareg(Surv(start,cum_balls , wicket) ~ 
      cumulative_runs_lt20 + cumulative_runs_ge20 +  cumulative_fours + ridge(cumulative_dot_balls) + cluster (id) , data = 
        NLTC_P_7_cut)) + theme(legend.position = "none") + ggtitle("Aalen plot of NLTC Perera for the 7th batting position")

NLTC_p8 <- autoplot(aareg(Surv(start,cum_balls , wicket) ~ 
      cumulative_runs_lt20 + cumulative_runs_ge20 +  cumulative_fours + ridge(cumulative_dot_balls) + cluster (id) , data = 
        NLTC_P_8_cut)) + theme(legend.position = "none") + ggtitle("Aalen plot of NLTC Perera for the 8th batting position")

NLTCAalenPos <- ggarrange(NLTC_p7,NLTC_p8, nrow = 2)
NLTCAalenPos
```

```{r,warning=FALSE,message=FALSE,results='hide'}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"NLTCAalenPos.eps"),width = 10,height = 7,horizontal = FALSE)
NLTCAalenPos
dev.off()
```

