---
title: "MDKJ_VEN"
author: "S_16_373"
date: "5/16/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Load the libraries**
```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(survival)
library(ggfortify)
library(survminer)
library(rms)
library(dynpred)
library(MASS)
library(CPE)
library(scatterplot3d)
library(plotly)
```
\
\
**Read the data sets**
```{r,warning=FALSE,message=FALSE}
Home <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Home/Home.csv")
Overseas <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Overseas/Overseas.csv")
```
\
\
**Merge two data sets**
```{r,warning=FALSE,message=FALSE}
data_merge <- rbind(Home , Overseas)
```
\
\
**Filter the data of MDKJ Perera**
```{r,warning=FALSE,message=FALSE}
bt10 <- data_merge %>% filter(grepl('MDKJ Perera' , Striker))
```
\
\
***1)Analysis for two different Venue***
\
\
```{r,message=FALSE,warning=FALSE}
MDKJ_diff_ven <- survdiff(Surv(cum_balls , wicket) ~ Venue, data = bt10)
MDKJ_diff_ven
```
The p value is greater than 0.05. Therefore we cannot see a significant difference between the Venue.

\
\
**Home**
\
\
**Filter the first Venue**
```{r,warning=FALSE,message=FALSE}
MDKJ_H <- bt10 %>% filter(Venue == "Home")
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
MDKJ_H_cut <- survSplit(MDKJ_H , cut = 40 , end = "cum_balls" , event = "wicket" , start = "start" , id = "id")

MDKJ_H_cut$hv1 <- MDKJ_H_cut$cum_singles * (MDKJ_H_cut$start < 40)
MDKJ_H_cut$hv2 <- MDKJ_H_cut$cum_singles * (MDKJ_H_cut$start >= 40)


cox_MDKJ_H_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                          hv1 + hv2 +cum_boundaries+ridge(cum_dotBalls) + cluster (id) , data = MDKJ_H_cut)

summary(cox_MDKJ_H_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_MDKJ_H <- cox.zph(cox_MDKJ_H_heav)
test_MDKJ_H
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_MDKJ_H <- ggadjustedcurves(cox_MDKJ_H_heav , data = MDKJ_H_cut , size = 2,
                          ggtheme = theme_survminer()) + 
                          geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +
                          ggtitle("Survival curve for MDKJ Perera for Venue Home") + 
                          theme(axis.title = element_text(size = 15),
                                axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_MDKJ_H <- ggforest(cox_MDKJ_H_heav , data = MDKJ_H_cut,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_MDKJ_H
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
                          hv1 + hv2 +cum_boundaries+ridge(cum_dotBalls) + cluster (id) , data = MDKJ_H_cut)
```
\
\
**Second Venue**
\
\
**Filter the second Venue**
```{r,warning=FALSE,message=FALSE}
MDKJ_O <- bt10 %>% filter(Venue == "Overseas")
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
MDKJ_O_cut <- survSplit(MDKJ_O , cut = 40 , end = "cum_balls" , event = "wicket" , start = "start" , id = "id")

MDKJ_O_cut$hv1 <- MDKJ_O_cut$cum_singles * (MDKJ_O_cut$start < 40)
MDKJ_O_cut$hv2 <- MDKJ_O_cut$cum_singles * (MDKJ_O_cut$start >= 40)


cox_MDKJ_O_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                           hv1 + hv2 +cum_boundaries+ridge(cum_dotBalls) + cluster (id) , data = MDKJ_O_cut)

summary(cox_MDKJ_O_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_MDKJ_O <- cox.zph(cox_MDKJ_O_heav)
test_MDKJ_O
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_MDKJ_O <- ggadjustedcurves(cox_MDKJ_O_heav , data = MDKJ_O_cut , size = 2,
                          ggtheme = theme_survminer()) + 
                          geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +
                          ggtitle("Survival curve for MDKJ Perera for Venue Overseas") + 
                          theme(axis.title = element_text(size = 15),
                                axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_MDKJ_O <- ggforest(cox_MDKJ_O_heav , data = MDKJ_O_cut,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_MDKJ_O
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
                           hv1 + hv2 +cum_boundaries+ridge(cum_dotBalls) + cluster (id) , data = MDKJ_O_cut)
```
\
\
**Survival curve**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,6)}
MDKJSurvPlotVen <- ggarrange(cox_plot_MDKJ_H,cox_plot_MDKJ_O,ncol = 2)
MDKJSurvPlotVen
```
\
\
**Upload to texStudio**
```{r,results='hide',message=FALSE,warning=FALSE}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"MDKJSurvPlotVen.eps"),width = 10,height = 7,horizontal = FALSE)
MDKJSurvPlotVen
dev.off()
```
\
\
**Aalen model**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,7)}
MDKJ_H_cut <- rename(MDKJ_H_cut,cumulative_singles_lt40 = hv1, cumulative_singles_ge40 = hv2 ,cumulative_fours = 
                    cum_boundaries,cumulative_dot_balls=cum_dotBalls)
MDKJ_O_cut <- rename(MDKJ_O_cut,cumulative_singles_lt40 = hv1, cumulative_singles_ge40 = hv2,cumulative_fours = 
                    cum_boundaries,cumulative_dot_balls=cum_dotBalls)

MDKJ_pH <- autoplot(aareg(Surv(start,cum_balls , wicket) ~ 
                           cumulative_singles_lt40 + cumulative_singles_ge40 +cumulative_fours+ridge(cumulative_dot_balls) + cluster (id) , data = MDKJ_H_cut)) +
  theme(legend.position = "none") + ggtitle("Aalen plot of MDKJ Perera for home venue")

MDKJ_pO <- autoplot(aareg(Surv(start,cum_balls , wicket) ~ 
                           cumulative_singles_lt40 + cumulative_singles_ge40 +cumulative_fours+ridge(cumulative_dot_balls) + cluster (id) , data = MDKJ_O_cut)) +
  theme(legend.position = "none") + ggtitle("Aalen plot of MDKJ Perera for overseas venue")

MDKJAalenVen <- ggarrange(MDKJ_pH,MDKJ_pO, nrow = 2)
MDKJAalenVen
```

```{r,warning=FALSE,message=FALSE,results='hide'}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"MDKJAalenVen.eps"),width = 10,height = 7,horizontal = FALSE)
MDKJAalenVen
dev.off()
```
