---
title: "MDKJ_POS"
author: "S_16_373"
date: "5/16/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Load the libraries**
```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(survival)
library(ggfortify)
library(survminer)
library(rms)
library(dynpred)
library(MASS)
library(CPE)
library(scatterplot3d)
library(plotly)
```
\
\
**Read the data sets**
```{r,warning=FALSE,message=FALSE}
Home <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Home/Home.csv")
Overseas <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Overseas/Overseas.csv")
```
\
\
**Merge two data sets**
```{r,warning=FALSE,message=FALSE}
data_merge <- rbind(Home , Overseas)
```
\
\
**Filter the data of MDKJ Perera**
```{r,warning=FALSE,message=FALSE}
bt10 <- data_merge %>% filter(grepl('MDKJ Perera' , Striker))
```
\
\
***1)Analysis for different batting position***
\
\
```{r,message=FALSE,warning=FALSE}
bt10_ps <- bt10 %>% filter(bat_position == c(1,2,3,4))

MDKJ_diff_pos <- survdiff(Surv(cum_balls , wicket) ~ bat_position, data = bt10_ps)
MDKJ_diff_pos
```
The p value is greater than 0.05. Therefore no significant difference between the batting positions 1,2,3 and 4.

\
\
**batting position 1**
\
\
**Filter the first bat_position**
```{r,warning=FALSE,message=FALSE}
MDKJ_P_1<- bt10 %>% filter(bat_position == 1)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
MDKJ_P_1_cut <- survSplit(MDKJ_P_1 , cut = 30 , end = "cum_balls" , event = "wicket" , start = "start" , id = "id")

MDKJ_P_1_cut$hv1 <- MDKJ_P_1_cut$cum_boundaries  * (MDKJ_P_1_cut$start < 30)
MDKJ_P_1_cut$hv2 <- MDKJ_P_1_cut$cum_boundaries  * (MDKJ_P_1_cut$start >= 30)

cox_MDKJ_P_1_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                             cum_runs +hv1 + hv2 + ridge(cum_dotBalls) + cluster (id) , data = MDKJ_P_1_cut)

summary(cox_MDKJ_P_1_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_MDKJ_P_1 <- cox.zph(cox_MDKJ_P_1_heav)
test_MDKJ_P_1
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_MDKJ_P_1 <- ggadjustedcurves(cox_MDKJ_P_1_heav , data = MDKJ_P_1_cut , size = 2,
                        ggtheme =theme_survminer()) + geom_hline(yintercept = c(0.25,0.5,0.75) ,
                        linetype = "dashed") +ggtitle("Survival curve for MDKJ Perera for the 1st
                        batting position") + theme(axis.title = element_text(size = 15),axis.text = 
                        element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_MDKJ_P_1 <- ggforest(cox_MDKJ_P_1_heav , data = MDKJ_P_1_cut,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_MDKJ_P_1
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
                             cum_runs +hv1 + hv2 + ridge(cum_dotBalls) + cluster (id) , data = MDKJ_P_1_cut)
```
\
\
**2nd batting position**
\
\
**Filter the second bat_position**
```{r,warning=FALSE,message=FALSE}
MDKJ_P_2 <- bt10 %>% filter(bat_position == 2)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
MDKJ_P_2_cut <- survSplit(MDKJ_P_2 , cut = 30 , end = "cum_balls" , event = "wicket" , start = "start" , id = "id")

MDKJ_P_2_cut$hv1 <- MDKJ_P_2_cut$cum_boundaries  * (MDKJ_P_2_cut$start < 30)
MDKJ_P_2_cut$hv2 <- MDKJ_P_2_cut$cum_boundaries  * (MDKJ_P_2_cut$start >= 30)

cox_MDKJ_P_2_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                             cum_runs +hv1 + hv2 + ridge(cum_dotBalls) + cluster (id) , data = MDKJ_P_2_cut)

summary(cox_MDKJ_P_2_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_MDKJ_P_2 <- cox.zph(cox_MDKJ_P_2_heav)
test_MDKJ_P_2
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_MDKJ_P_2 <- ggadjustedcurves(cox_MDKJ_P_2_heav , data = MDKJ_P_2_cut , size = 2,ggtheme = 
                        theme_survminer()) + geom_hline(yintercept = c(0.25,0.5,0.75) , 
                        linetype = "dashed") +ggtitle("Survival curve for MDKJ Perera for 
                        the 2nd batting position") + theme(axis.title = element_text(size = 15),
                        axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_MDKJ_P_2 <- ggforest(cox_MDKJ_P_2_heav , data = MDKJ_P_2_cut,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_MDKJ_P_2
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
                             cum_runs +hv1 + hv2 + ridge(cum_dotBalls) + cluster (id) , data = MDKJ_P_2_cut)
```
\
\
**batting position 3**
\
\
**Filter the first bat_position**
```{r,warning=FALSE,message=FALSE}
MDKJ_P_3<- bt10 %>% filter(bat_position == 3)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
MDKJ_P_3_cut <- survSplit(MDKJ_P_3 , cut = 30 , end = "cum_balls" , event = "wicket" , start = "start" , id = "id")

MDKJ_P_3_cut$hv1 <- MDKJ_P_3_cut$cum_boundaries  * (MDKJ_P_3_cut$start < 30)
MDKJ_P_3_cut$hv2 <- MDKJ_P_3_cut$cum_boundaries  * (MDKJ_P_3_cut$start >= 30)

cox_MDKJ_P_3_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                             cum_runs +hv1 + hv2 + ridge(cum_dotBalls) + cluster (id) , data = MDKJ_P_3_cut)


summary(cox_MDKJ_P_3_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_MDKJ_P_3 <- cox.zph(cox_MDKJ_P_3_heav)
test_MDKJ_P_3
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_MDKJ_P_3 <- ggadjustedcurves(cox_MDKJ_P_3_heav , data = MDKJ_P_3_cut , size = 2,
                        ggtheme =theme_survminer()) + geom_hline(yintercept = c(0.25,0.5,0.75) ,
                        linetype = "dashed") +ggtitle("Survival curve for MDKJ Perera for the 3rd
                        batting position") + theme(axis.title = element_text(size = 15),axis.text = 
                        element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_MDKJ_P_3 <- ggforest(cox_MDKJ_P_3_heav , data = MDKJ_P_3_cut,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_MDKJ_P_3
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
                             cum_runs +hv1 + hv2 + ridge(cum_dotBalls) + cluster (id) , data = MDKJ_P_3_cut)
```
\
\
**batting position 4**
\
\
**Filter the first bat_position**
```{r,warning=FALSE,message=FALSE}
MDKJ_P_4<- bt10 %>% filter(bat_position == 4)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
MDKJ_P_4_cut <- survSplit(MDKJ_P_4 , cut = 30 , end = "cum_balls" , event = "wicket" , start = "start" , id = "id")

MDKJ_P_4_cut$hv1 <- MDKJ_P_4_cut$cum_boundaries  * (MDKJ_P_4_cut$start < 30)
MDKJ_P_4_cut$hv2 <- MDKJ_P_4_cut$cum_boundaries  * (MDKJ_P_4_cut$start >= 30)

cox_MDKJ_P_4_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                             cum_runs +hv1 + hv2 + ridge(cum_dotBalls) + cluster (id) , data = MDKJ_P_4_cut)

summary(cox_MDKJ_P_4_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_MDKJ_P_4 <- cox.zph(cox_MDKJ_P_4_heav)
test_MDKJ_P_4
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_MDKJ_P_4 <- ggadjustedcurves(cox_MDKJ_P_4_heav , data = MDKJ_P_4_cut , size = 2,
                        ggtheme =theme_survminer()) + geom_hline(yintercept = c(0.25,0.5,0.75) ,
                        linetype = "dashed") +ggtitle("Survival curve for MDKJ Perera for the 4th
                        batting position") + theme(axis.title = element_text(size = 15),axis.text = 
                        element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_MDKJ_P_4 <- ggforest(cox_MDKJ_P_4_heav , data = MDKJ_P_4_cut,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_MDKJ_P_4
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
                             cum_runs +hv1 + hv2 + ridge(cum_dotBalls) + cluster (id) , data = MDKJ_P_4_cut)
```
\
\
**Survival curve**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,6)}
MDKJSurvPlotPos <- ggarrange(cox_plot_MDKJ_P_1,cox_plot_MDKJ_P_2,cox_plot_MDKJ_P_3,cox_plot_MDKJ_P_4,ncol  = 2)
MDKJSurvPlotPos
```
\
\
**Upload to texStudio**
```{r,results='hide',message=FALSE,warning=FALSE}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"MDKJSurvPlotPos.eps"),width = 10,height = 7,horizontal = FALSE)
MDKJSurvPlotPos
dev.off()
```
\
\
**Aalen model**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,7)}
MDKJ_P_1_cut <- rename(MDKJ_P_1_cut,cumulative_runs=cum_runs,cumulative_fours_lt30 = hv1, cumulative_fours_ge30 = hv2, 
                       cumulative_dot_balls=cum_dotBalls)
MDKJ_P_2_cut <- rename(MDKJ_P_2_cut,cumulative_runs=cum_runs,cumulative_fours_lt30 = hv1, cumulative_fours_ge30 = hv2, 
                       cumulative_dot_balls=cum_dotBalls)
MDKJ_P_3_cut <- rename(MDKJ_P_3_cut,cumulative_runs=cum_runs,cumulative_fours_lt30 = hv1, cumulative_fours_ge30 = hv2, 
                       cumulative_dot_balls=cum_dotBalls)
MDKJ_P_4_cut <- rename(MDKJ_P_4_cut,cumulative_runs=cum_runs,cumulative_fours_lt30 = hv1, cumulative_fours_ge30 = hv2, 
                       cumulative_dot_balls=cum_dotBalls)

MDKJ_p1 <- autoplot(aareg(Surv(start,cum_balls , wicket) ~ 
                             cumulative_runs +cumulative_fours_lt30 + cumulative_fours_ge30 + ridge(cumulative_dot_balls) + 
                            cluster (id) , data = MDKJ_P_1_cut)) + 
  theme(legend.position = "none") + ggtitle("Aalen plot of MDKJ Perera for the 1st batting position")

MDKJ_p2 <- autoplot(aareg(Surv(start,cum_balls , wicket) ~ 
                             cumulative_runs +cumulative_fours_lt30 + cumulative_fours_ge30 + ridge(cumulative_dot_balls) + 
                            cluster (id) , data = MDKJ_P_2_cut))+ 
  theme(legend.position = "none") + ggtitle("Aalen plot of MDKJ Perera for the 2nd batting position")

MDKJ_p3 <- autoplot(aareg(Surv(start,cum_balls , wicket) ~ 
                             cumulative_runs +cumulative_fours_lt30 + cumulative_fours_ge30 + ridge(cumulative_dot_balls) + 
                            cluster (id) , data = MDKJ_P_3_cut))+ 
  theme(legend.position = "none") + ggtitle("Aalen plot of MDKJ Perera for the 3rd batting position")

MDKJ_p4 <- autoplot(aareg(Surv(start,cum_balls , wicket) ~ 
                             cumulative_runs +cumulative_fours_lt30 + cumulative_fours_ge30 + ridge(cumulative_dot_balls) + 
                            cluster (id) , data = MDKJ_P_4_cut))+ 
  theme(legend.position = "none") + ggtitle("Aalen plot of MDKJ Perera for the 4th batting position")

MDKJAalenPos <- ggarrange(MDKJ_p1,MDKJ_p2,MDKJ_p3,MDKJ_p4, nrow = 4)
MDKJAalenPos
```

```{r,warning=FALSE,message=FALSE,results='hide'}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"MDKJAalenPos.eps"),width = 10,height = 7,horizontal = FALSE)
MDKJAalenPos
dev.off()
```

