---
title: "ND_VEN"
author: "S_16_373"
date: "5/16/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


**Load the libraries**
```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(survival)
library(ggfortify)
library(survminer)
library(rms)
library(dynpred)
library(MASS)
library(CPE)
library(scatterplot3d)
library(plotly)
```
\
\
**Read the data sets**
```{r,warning=FALSE,message=FALSE}
Home <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Home/Home.csv")
Overseas <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Overseas/Overseas.csv")
```
\
\
**Merge two data sets**
```{r,warning=FALSE,message=FALSE}
data_merge <- rbind(Home , Overseas)
```
\
\
**Filter the data of N Dickwella**
```{r,warning=FALSE,message=FALSE}
bt11 <- data_merge %>% filter(grepl('N Dickwella' , Striker))
```
\
\
***1)Analysis for two different Venue***
\
\
```{r,message=FALSE,warning=FALSE}
ND_diff_ven <- survdiff(Surv(cum_balls , wicket) ~ Venue, data = bt11)
ND_diff_ven
```
The p value is less than 0.05. Therefore we have a significant difference between the Venue.

\
\
**Home**
\
\
**Filter the first Venue**
```{r,warning=FALSE,message=FALSE}
ND_H <- bt11 %>% filter(Venue == "Home")
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
cox_ND_H_new <- coxph(Surv(cum_balls , wicket) ~ 
                    cum_singles+cum_doubles+ridge(cum_dotBalls), data = ND_H)

summary(cox_ND_H_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_ND_H <- cox.zph(cox_ND_H_new)
test_ND_H
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_ND_H <- ggadjustedcurves(cox_ND_H_new , data = ND_H , size = 2,
                          ggtheme = theme_survminer()) + 
                          geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +
                          ggtitle("Survival curve for N Dickwella for Venue Home") + 
                          theme(axis.title = element_text(size = 15),
                                axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_ND_H <- ggforest(cox_ND_H_new , data = ND_H,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_ND_H
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(cum_balls , wicket) ~ 
                    cum_singles+cum_doubles+ridge(cum_dotBalls), data = ND_H)
```
\
\
**Second Venue**
\
\
**Filter the second Venue**
```{r,warning=FALSE,message=FALSE}
ND_O <- bt11 %>% filter(Venue == "Overseas")
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
cox_ND_O_new <- coxph(Surv(cum_balls , wicket) ~ 
                        cum_singles+cum_doubles+ridge(cum_dotBalls), data = ND_O)

summary(cox_ND_O_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_ND_O <- cox.zph(cox_ND_O_new)
test_ND_O
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_ND_O <- ggadjustedcurves(cox_ND_O_new , data = ND_O , size = 2,
                          ggtheme = theme_survminer()) + 
                          geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +
                          ggtitle("Survival curve for N Dickwella for Venue Overseas") + 
                          theme(axis.title = element_text(size = 15),
                                axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_ND_O <- ggforest(cox_ND_O_new , data = ND_O,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_ND_O
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(cum_balls , wicket) ~ 
                        cum_singles+cum_doubles+ridge(cum_dotBalls), data = ND_O)
```
\
\
**Survival curve**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,6)}
NDSurvPlotVen <- ggarrange(cox_plot_ND_H,cox_plot_ND_O,ncol = 2)
NDSurvPlotVen
```
\
\
**Upload to texStudio**
```{r,results='hide',message=FALSE,warning=FALSE}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"NDSurvPlotVen.eps"),width = 10,height = 7,horizontal = FALSE)
NDSurvPlotVen
dev.off()
```
\
\
**Aalen model**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,7)}
ND_H <- rename(ND_H,cumulative_singles = cum_singles, cumulative_doubles = cum_doubles,cumulative_dot_balls=cum_dotBalls)
ND_O <- rename(ND_O,cumulative_singles = cum_singles, cumulative_doubles = cum_doubles,cumulative_dot_balls=cum_dotBalls)

ND_pH <- autoplot(aareg(Surv(cum_balls , wicket) ~ 
                        cumulative_singles+cumulative_doubles+ridge(cumulative_dot_balls), data = ND_H)) +
  theme(legend.position = "none") + ggtitle("Aalen plot of N Dickwella for home venue")

ND_pO <- autoplot(aareg(Surv(cum_balls , wicket) ~ 
                        cumulative_singles+cumulative_doubles+ridge(cumulative_dot_balls), data = ND_O))+
  theme(legend.position = "none") + ggtitle("Aalen plot of N Dickwella for overseas venue")

NDAalenVen <- ggarrange(ND_pH,ND_pO, nrow = 2)
NDAalenVen
```

```{r,warning=FALSE,message=FALSE,results='hide'}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"NDAalenVen.eps"),width = 10,height = 7,horizontal = FALSE)
NDAalenVen
dev.off()
```
