---
title: "EDA_New"
author: "S_16_373"
date: "7/3/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Load the libraries**
```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(ggfortify)
library(ggplot2)
library(lubridate)
library(tidytext)
library(ggpubr)
```

**Read the data set and merge**
```{r,warning=FALSE,message=FALSE}
Home <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Home/Home.csv")
Overseas <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Overseas/Overseas.csv")

data_merge <- rbind(Home , Overseas)
```

**Filter rows that contains batsman, bowler and all rounder data**
```{r,warning=FALSE,message=FALSE}
batsman <- data_merge %>% filter(grepl('batsman' , Striker_status))
bowler <- data_merge %>% filter(grepl('bowler' , Striker_status))
allRounder <- data_merge %>% filter(grepl('all rounder' , Striker_status))
```


**Filter rows that contains analysing players**
```{r,warning=FALSE,message=FALSE}
bat_ana <- batsman %>% filter(grepl('BKG Mendis|LD Chandimal|MDKJ Perera|N Dickwella|WU Tharanga' , Striker))
all_ana <- allRounder %>% filter(grepl('AD Mathews|DM de Silva|MD Gunathilaka|NLTC Perera' , Striker))
```

**Select only specific columns**
```{r,warning=FALSE,message=FALSE}
bat_ana1 <- bat_ana %>% dplyr::select(Match_Number,Venue,Striker,batsman_runs)
all_ana1 <- all_ana %>% dplyr::select(Match_Number,Venue,Striker,batsman_runs)

```

**Total runs per match**
```{r,warning=FALSE,message=FALSE}
bat_ana1 <- bat_ana1 %>% group_by(Venue,Match_Number , Striker) %>%
  summarise(total_runs = sum(batsman_runs , na.rm = TRUE))


all_ana1 <- all_ana1 %>% group_by(Venue,Match_Number , Striker) %>%
  summarise(total_runs = sum(batsman_runs , na.rm = TRUE))
```

```{r,warning=FALSE,message=FALSE}
pd = position_dodge(0.85)
```

**Venue**
**Batsman**
```{r,warning=FALSE,message=FALSE,fig.width=9}
match_ana_1 <- bat_ana1 %>% group_by(Venue,Striker) %>% 
  summarise(Count = n(),total_runs=max(total_runs)+0.05*diff(range(total_runs)))

b_ana1 <- ggplot(bat_ana1,aes(x = reorder(Striker , total_runs), y = total_runs,fill = Venue)) + 
  geom_boxplot() + 
        stat_summary(fun.y = mean, geom = "point", shape =18, size=4,colour = "brown4", 
                     position = pd, show.legend = FALSE) +
        geom_text(data = match_ana_1,
            aes(label = paste0("n = ", Count)), position = pd, size = 4, show.legend = FALSE) + 
  theme(axis.text.x = element_text(face = "bold",angle = 90),axis.text = element_text(size = 14),
        axis.title = element_text(size = 15),legend.title = element_text(size = 20),legend.text = element_text(size = 15)) + xlab("Striker")+ylab("Runs Scored") +
  ggtitle("Runs scored by batsman for different venues") 

b_ana1
```

**Upload to texStudio**
```{r,results='hide',message=FALSE,warning=FALSE}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"bat_ven_new.eps"),width = 10,height = 7,horizontal = FALSE)
b_ana1
dev.off()
```



**All Rounder**
```{r,warning=FALSE,message=FALSE,fig.width=10}
match_ana_3 <- all_ana1 %>% group_by(Venue,Striker) %>% 
  summarise(Count = n(),total_runs=max(total_runs)+0.05*diff(range(total_runs)))

b_ana3 <- ggplot(all_ana1,aes(x = reorder(Striker , total_runs), y = total_runs,fill = Venue))+
  geom_boxplot() + 
        stat_summary(fun.y = mean, geom = "point", shape =18, size=4,colour = "brown4",
                     position = pd, show.legend = FALSE) +
        geom_text(data = match_ana_3,
            aes(label = paste0("n = ", Count)), position = pd, size = 4, show.legend = FALSE) + 
  theme(axis.text.x = element_text(face = "bold",angle = 90),axis.text = element_text(size = 14),
        legend.title = element_text(size = 20),axis.title = element_text(size = 15),
        legend.text = element_text(size = 15)) + xlab("Striker")+ylab("Runs Scored") +
  ggtitle("Runs scored by allrounders for different venues")

b_ana3
```


**Upload to texStudio**
```{r,results='hide',message=FALSE,warning=FALSE}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"all_ven_new.eps"),width = 10,height = 7,horizontal = FALSE)
b_ana3
dev.off()
```

**Innings**
**Batsman**
**Select only specific columns**
```{r,warning=FALSE,message=FALSE}
bat_ana2 <- bat_ana %>% select(Venue,Match_Number,innings,Striker,batsman_runs)
all_ana2 <- all_ana %>% select(Venue,Match_Number,innings,Striker,batsman_runs)
```


**Total runs per match**
```{r,warning=FALSE,message=FALSE}
bat_ana2 <- bat_ana2 %>% group_by(Venue,innings,Match_Number,Striker) %>% 
  summarise(total_runs = sum(batsman_runs, na.rm = TRUE))

all_ana2 <- all_ana2 %>% group_by(Venue,innings,Match_Number,Striker) %>% 
  summarise(total_runs = sum(batsman_runs, na.rm = TRUE))
```

**Batsman**
```{r,warning=FALSE,message=FALSE,fig.width=9}
match_ana_4 <- bat_ana2 %>% group_by(innings,Striker) %>% 
  summarise(Count = n(),total_runs=max(total_runs)+0.05*diff(range(total_runs)))


b_ana4 <- ggplot(bat_ana2,aes(x = reorder(Striker , total_runs), y =total_runs,
                          fill = as.factor(innings)))+ geom_boxplot() + 
      stat_summary(fun.y = mean, geom = "point", shape =18, size=4,colour = "brown4",
                   position = pd, show.legend = FALSE) +
      geom_text(data = match_ana_4,
            aes(label = paste0("n = ", Count)), position = pd, size = 4,show.legend = FALSE) + 
      theme(axis.text.x = element_text(face = "bold",angle = 90),axis.text = element_text(size = 14),
            legend.title = element_text(size = 20),axis.title = element_text(size = 15),
            legend.text = element_text(size = 15)) + xlab("Striker")+ylab("Runs Scored") +
      scale_fill_discrete(name = "Innings")

b_ana4
```

**Upload to texStudio**
```{r,results='hide',message=FALSE,warning=FALSE}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"bat_inn_new.eps"),width = 10,height = 7,horizontal = FALSE)
b_ana4
dev.off()
```


**All Rounder**
```{r,warning=FALSE,message=FALSE,fig.width=10}
match_ana_6 <- all_ana2 %>% group_by(innings,Striker) %>% 
  summarise(Count = n(),total_runs=max(total_runs)+0.05*diff(range(total_runs)))

b_ana6 <- ggplot(all_ana2,aes(x = Striker , total_runs,
                             fill = as.factor(innings)))+ geom_boxplot() + 
      stat_summary(fun.y = mean, geom = "point", shape =18, size=4,colour = "brown4",
                   position = pd, show.legend = FALSE) +
      geom_text(data = match_ana_6,
            aes(label = paste0("n = ", Count)), position = pd, size = 4, show.legend = FALSE) + 
      theme(axis.text.x = element_text(face = "bold",angle = 90),axis.text = element_text(size = 14),
            legend.title = element_text(size = 20),axis.title = element_text(size = 15),
            legend.text = element_text(size = 15)) + xlab("Striker")+ylab("Runs Scored") +
      scale_fill_discrete(name = "Innings")

b_ana6
```

**Upload to texStudio**
```{r,results='hide',message=FALSE,warning=FALSE}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"all_inn_new.eps"),width = 10,height = 7,horizontal = FALSE)
b_ana6
dev.off()
```

**c) Boxplots for batsman,bowlers and allrounders for different batting positions**
\
**Select only specific columns**
```{r,warning=FALSE,message=FALSE}
bat_ana3 <- bat_ana %>% select(Venue,Match_Number,innings,Striker,batsman_runs,bat_position)
all_ana3 <- all_ana %>% select(Venue,Match_Number,innings,Striker,batsman_runs,bat_position)
```
\
**Total runs per match**
```{r,warning=FALSE,message=FALSE}
bat_ana3 <- bat_ana3 %>% group_by(Venue,innings,bat_position,Match_Number,Striker) %>% 
  summarise(total_runs = sum(batsman_runs, na.rm = TRUE))

all_ana3 <- all_ana3 %>% group_by(Venue,innings,bat_position,Match_Number,Striker) %>% 
  summarise(total_runs = sum(batsman_runs, na.rm = TRUE))
```

**Batsman**
```{r,warning=FALSE,message=FALSE,fig.width=12}
match_ana_7 <- bat_ana3 %>% group_by(bat_position,Striker) %>% 
  summarise(Count = n(),total_runs=max(total_runs)+0.05*diff(range(total_runs)))


b_ana7 <- ggplot(bat_ana3,aes(x = reorder(Striker , total_runs), y = total_runs,
                          fill = as.factor(bat_position))) + geom_boxplot() + 
      stat_summary(fun.y = mean, geom = "point", shape =18, size=4,colour ="brown4",
                   position = pd, show.legend = FALSE) +
      geom_text(data = match_ana_7,
            aes(label = paste0("n = ", Count)), position = pd, size = 4, show.legend = FALSE) + 
      theme(axis.text.x = element_text(face = "bold",angle = 90),axis.text = element_text(size = 14),
            legend.title = element_text(size = 20),axis.title = element_text(size = 15),
            legend.text = element_text(size = 15)) +xlab("Striker")+ylab("Runs Scored") +
      scale_fill_discrete(name = "Batting Position")

b_ana7
```

**Upload to texStudio**
```{r,results='hide',message=FALSE,warning=FALSE}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"bat_pos_new.eps"),width = 10,height = 7,horizontal = FALSE)
b_ana7
dev.off()
```



**All Rounder**
```{r,warning=FALSE,message=FALSE,fig.width=12}
match_ana_9 <- all_ana3 %>% group_by(bat_position,Striker) %>% 
  summarise(Count = n(),total_runs=max(total_runs)+0.05*diff(range(total_runs)))

b_ana9 <- ggplot(all_ana3,aes(x = Striker , total_runs,fill = as.factor(bat_position)))+
  geom_boxplot() + 
      stat_summary(fun.y = mean, geom = "point", shape =18, size=4,colour ="brown4",
                   position = pd, show.legend = FALSE) +
      geom_text(data = match_ana_9,
            aes(label = paste0("n = ", Count)), position = pd, size = 4, show.legend = FALSE) + 
      theme(axis.text.x = element_text(face = "bold",angle = 90),axis.text = element_text(size = 14),
            legend.title = element_text(size = 20),
            legend.text = element_text(size = 15)) +xlab("Striker")+ylab("Runs Scored") +
      scale_fill_discrete(name = "Batting Position")

b_ana9
```

**Upload to texStudio**
```{r,results='hide',message=FALSE,warning=FALSE}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"all_pos_new.eps"),width = 10,height = 7,horizontal = FALSE)
b_ana9
dev.off()
```