---
title: "AUC_test"
author: "S_16_373"
date: "2/22/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Load the libraries**
```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(survival)
library(ggfortify)
library(survminer)
library(rms)
library(dynpred)
library(MASS)
library(CPE)
library(scatterplot3d)
library(plotly)
```
\
\
**Read the data sets**
```{r,warning=FALSE,message=FALSE}
Home <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Home/Home.csv")
Overseas <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Overseas/Overseas.csv")
```
\
\
**Merge two data sets**
```{r,warning=FALSE,message=FALSE}
data_merge <- rbind(Home , Overseas)
```
\
\
**Filter the data of LD Chandimal**
```{r,warning=FALSE,message=FALSE}
bt1 <- data_merge %>% filter(grepl('LD Chandimal' , Striker))
```
\
\
***1)Analysis for two different innings***
\
\
**First innings**
\
\
**Filter the first innings**
```{r,warning=FALSE,message=FALSE}
LDC_1 <- bt1 %>% filter(innings == 1)
```
\
\
**Cox model for first innings**
```{r,warning=FALSE,message=FALSE}
cox_LDC_1 <- coxph(Surv(cum_balls , wicket == 1) ~ 
                     cum_runs+cum_singles+cum_doubles+cum_boundaries+ridge(cum_dotBalls), data = LDC_1)
summary(cox_LDC_1)
```
\
\
**Finding the best model using AIC**
```{r,warning=FALSE,message=FALSE}
model_LDC_1 <- stepAIC(cox_LDC_1)
```
\
\
**Best Model**
```{r,warning=FALSE,message=FALSE}
cox_LDC_1_new <- coxph(Surv(cum_balls , wicket) ~ 
                         cum_singles + cum_doubles +  ridge(cum_dotBalls), data = LDC_1)
summary(cox_LDC_1_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_LDC_1 <- cox.zph(cox_LDC_1_new)
test_LDC_1
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_LDC_1 <- ggadjustedcurves(cox_LDC_1_new , data = LDC_1 , size = 2,ggtheme = theme_survminer()) + 
                  geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +xlim(0,70) +
                    ggtitle("Survival curve for LD Chandimal for the first innings") +
                    theme(text = element_text(size = 20))

cox_plot_LDC_1
```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE}
coef_plot_LDC_1 <- ggforest(cox_LDC_1_new , data = LDC_1,fontsize = 1.2)
coef_plot_LDC_1
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(cum_balls , wicket) ~ 
      cum_singles + cum_doubles + cum_boundaries+ ridge(cum_dotBalls), data = LDC_1)
```
\
\
**percentage of matches won when the player is in the specific match**
```{r,warning=FALSE,message=FALSE}
match_status_LDC_1 <- unique(LDC_1[c("Match_Number","winning_status")])
tot_matches_LDC_1 <- nrow(match_status_LDC_1)
win_matches_LDC_1 <- sum(match_status_LDC_1$winning_status==1)

win_percent_LDC_1 <- (win_matches_LDC_1/tot_matches_LDC_1)*100

win_percent_LDC_1
```
\
\
**Runs contributed**
```{r,warning=FALSE,message=FALSE}
match_played_LDC_1 <- data_merge %>% filter(Match_Number %in% unique(LDC_1$Match_Number))
tot_runs_LDC_1 <- match_played_LDC_1 %>% summarise(sum_runs = sum(tot_runs))
LDC_runs_1 <- LDC_1 %>%  summarise(sum_runs = sum(tot_runs))

runs_contrib_percent_LDC_1 <- (LDC_runs_1/tot_runs_LDC_1)*100
runs_contrib_percent_LDC_1
```
\
\
**Second Innings**
\
\
**Filter the second innings**
```{r,warning=FALSE,message=FALSE}
LDC_2 <- bt1 %>% filter(innings == 2)
```
\
\
**Cox model for second innings**
```{r,warning=FALSE,message=FALSE}
cox_LDC_2 <- coxph(Surv(cum_balls , wicket) ~ 
                     cum_runs+cum_singles+cum_doubles+cum_boundaries+ridge(cum_dotBalls), data = LDC_2)
summary(cox_LDC_2)
```
\
\
**Finding the best model using AIC**
```{r,warning=FALSE,message=FALSE}
model_LDC_2 <- stepAIC(cox_LDC_2)
```
\
\
**Best Model**
```{r,warning=FALSE,message=FALSE}
cox_LDC_2_new <- coxph(Surv(cum_balls , wicket) ~ 
                         cum_runs + cum_singles + cum_boundaries+ ridge(cum_dotBalls), data = LDC_2)
summary(cox_LDC_2_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_LDC_2 <- cox.zph(cox_LDC_2_new)
test_LDC_2
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_LDC_2 <- ggadjustedcurves(cox_LDC_2_new , data = LDC_2 , size = 2,ggtheme = theme_survminer()) + 
                  geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +xlim(0,60) +
                    ggtitle("Survival curve for LD Chandimal for the second innings") +
                    theme(text = element_text(size = 20))

cox_plot_LDC_2
```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE}
coef_plot_LDC_2 <- ggforest(cox_LDC_2_new , data = LDC_2,fontsize = 1.2)
coef_plot_LDC_2
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(cum_balls , wicket) ~ 
      cum_singles + cum_doubles + cum_boundaries+ ridge(cum_dotBalls), data = LDC_2)
```
\
\
**percentage of matches won when the player is in the specific match**
```{r,warning=FALSE,message=FALSE}
match_status_LDC_2 <- unique(LDC_2[c("Match_Number","winning_status")])
tot_matches_LDC_2 <- nrow(match_status_LDC_2)
win_matches_LDC_2 <- sum(match_status_LDC_2$winning_status==1)

win_percent_LDC_2 <- (win_matches_LDC_2/tot_matches_LDC_2)*100

win_percent_LDC_2
```
\
\
**Runs contributed**
```{r,warning=FALSE,message=FALSE}
match_played_LDC_2 <- data_merge %>% filter(Match_Number %in% unique(LDC_2$Match_Number))
tot_runs_LDC_2 <- match_played_LDC_2 %>% summarise(sum_runs = sum(tot_runs))
LDC_runs_2 <- LDC_2 %>%  summarise(sum_runs = sum(tot_runs))

runs_contrib_percent_LDC_2 <- (LDC_runs_2/tot_runs_LDC_2)*100
runs_contrib_percent_LDC_2
```
\
\
\
***Compare different innings***
\
\
**Create the data frame**
```{r,warning=FALSE,message=FALSE}
PlayerName_LDC <- "LD Chandimal"
Innings <- c(1,2)
Survival_prob_LDC <- c(0.9629885,0.936521)
winning_percent_LDC <- c(19.23077,7.692308)
runs_contrib_percent_LDC <- c(14.96176,12.32639)

comp_innings_LDC <- data.frame(PlayerName_LDC,Innings,Survival_prob_LDC,runs_contrib_percent_LDC,winning_percent_LDC)
names(comp_innings_LDC) <- c("PlayerName","Innings","Survival_prob","runs_contrib_percent","winning_percent")
comp_innings_LDC
```
\
\
