---
title: "LD_INN"
author: "S_16_373"
date: "5/8/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Load the libraries**
```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(survival)
library(ggfortify)
library(survminer)
library(rms)
library(dynpred)
library(MASS)
library(CPE)
library(scatterplot3d)
library(plotly)
```
\
\
**Read the data sets**
```{r,warning=FALSE,message=FALSE}
Home <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Home/Home.csv")
Overseas <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Overseas/Overseas.csv")
```
\
\
**Merge two data sets**
```{r,warning=FALSE,message=FALSE}
data_merge <- rbind(Home , Overseas)
```
\
\
**Filter the data of LD Chandimal**
```{r,warning=FALSE,message=FALSE}
bt1 <- data_merge %>% filter(grepl('LD Chandimal' , Striker))
```
\
\
***1)Analysis for two different innings***
\
\
```{r,message=FALSE,warning=FALSE}
LD_diff_inn <- survdiff(Surv(cum_balls , wicket) ~ innings, data = bt1)
LD_diff_inn
```
The p value is less than 0.05. Therefore there is a significant difference between the innings.

\
\
**First innings**
\
\
**Filter the first innings**
```{r,warning=FALSE,message=FALSE}
LD_1 <- bt1 %>% filter(innings == 1)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
cox_LDC_1_new <- coxph(Surv(cum_balls , wicket) ~ 
                          cum_singles + cum_boundaries+ ridge(cum_dotBalls), data = LDC_1)

summary(cox_LDC_1_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_LD_1 <- cox.zph(cox_LDC_1_new)
test_LD_1
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_LD_1 <- ggadjustedcurves(cox_LDC_1_new , data = LD_1 , size = 2,
                      ggtheme = theme_survminer()) + 
                      geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +
                      ggtitle("Survival curve for LD Chandimal for the first innings") + 
                      theme(axis.title = element_text(size = 15),
                            axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_LD_1 <- ggforest(cox_LDC_1_new , data = LD_1,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_LD_1
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(cum_balls , wicket) ~ 
      cum_singles + cum_boundaries+ ridge(cum_dotBalls), data = LDC_1)
```
\
\
**Second Innings**
\
\
**Filter the second innings**
```{r,warning=FALSE,message=FALSE}
LD_2 <- bt1 %>% filter(innings == 2)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
cox_LDC_2_new <- coxph(Surv(cum_balls , wicket) ~ 
                          cum_singles + cum_boundaries+ ridge(cum_dotBalls), data = LDC_2)
summary(cox_LDC_2_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_LD_2 <- cox.zph(cox_LDC_2_new)
test_LD_2
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_LD_2 <- ggadjustedcurves(cox_LDC_2_new , data = LD_2 , size = 2,
                        ggtheme = theme_survminer()) + 
                        geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +
                        ggtitle("Survival curve for LD Chandimal for the second innings") + 
                        theme(axis.title = element_text(size = 15),
                              axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_LD_2 <- ggforest(cox_LDC_2_new , data = LD_2,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_LD_2
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(cum_balls , wicket) ~ 
      cum_singles + cum_boundaries+ ridge(cum_dotBalls), data = LDC_2)
```
\
\
**Survival curve**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,6)}
LDSurvPlotInn <- ggarrange(cox_plot_LD_1,cox_plot_LD_2,ncol = 2)
LDSurvPlotInn
```
\
\
**Upload to texStudio**
```{r,results='hide',message=FALSE,warning=FALSE}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"LDSurvPlotInn.eps"),width = 10,height = 7,horizontal = FALSE)
LDSurvPlotInn
dev.off()
```
\
\
**Aalen model**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,7)}
LDC_1 <- rename(LDC_1,cumulative_singles = cum_singles, cumulative_fours = cum_boundaries,cumulative_dot_balls=cum_dotBalls)
LDC_2 <- rename(LDC_2,cumulative_singles = cum_singles, cumulative_fours = cum_boundaries,cumulative_dot_balls=cum_dotBalls)

LD_p1 <- autoplot(aareg(Surv(cum_balls , wicket) ~ 
                          cumulative_singles + cumulative_fours+ ridge(cumulative_dot_balls), data = LDC_1))+ 
  theme(legend.position = "none") + ggtitle("Aalen plot of LD Chandimal for the first innings") 

LD_p2 <- autoplot(aareg(Surv(cum_balls , wicket) ~ 
                          cumulative_singles + cumulative_fours+ ridge(cumulative_dot_balls), data = LDC_2))+ 
  theme(legend.position = "none") + ggtitle("Aalen plot of LD Chandimal for the second innings") 

LDAalenInn <- ggarrange(LD_p1,LD_p2, nrow = 2)
LDAalenInn
```

```{r,warning=FALSE,message=FALSE,results='hide'}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"LDAalenInn.eps"),width = 10,height = 7,horizontal = FALSE)
LDAalenInn
dev.off()
```