---
title: "LD_POS"
author: "S_16_373"
date: "5/8/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Load the libraries**
```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(survival)
library(ggfortify)
library(survminer)
library(rms)
library(dynpred)
library(MASS)
library(CPE)
library(scatterplot3d)
library(plotly)
```
\
\
**Read the data sets**
```{r,warning=FALSE,message=FALSE}
Home <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Home/Home.csv")
Overseas <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Overseas/Overseas.csv")
```
\
\
**Merge two data sets**
```{r,warning=FALSE,message=FALSE}
data_merge <- rbind(Home , Overseas)
```
\
\
**Filter the data of LD Chandimal**
```{r,warning=FALSE,message=FALSE}
bt1 <- data_merge %>% filter(grepl('LD Chandimal' , Striker))
```
\
\
***1)Analysis for different batting position***
\
\
```{r,message=FALSE,warning=FALSE}
bt1_ps <- bt1 %>% filter(bat_position == c(3,4,5))

LD_diff_pos <- survdiff(Surv(cum_balls , wicket) ~ bat_position, data = bt1_ps)
LD_diff_pos
```
The p value is less than 0.05. Therefore there is a significant difference between the batting positions 3,4 and 5.
\
\
**batting position 3**
\
\
**Filter the first bat_position**
```{r,warning=FALSE,message=FALSE}
LD_P_3<- bt1 %>% filter(bat_position == 3)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
cox_LD_P_3_new <- coxph(Surv(cum_balls , wicket) ~ 
                          cum_singles + cum_doubles + cum_boundaries+ridge(cum_dotBalls), data = LD_P_3)

summary(cox_LD_P_3_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_LD_P_3 <- cox.zph(cox_LD_P_3_new)
test_LD_P_3
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_LD_P_3 <- ggadjustedcurves(cox_LD_P_3_new , data = LD_P_3 , size = 2,
                        ggtheme =theme_survminer()) + geom_hline(yintercept = c(0.25,0.5,0.75) ,
                        linetype = "dashed") +ggtitle("Survival curve for LD Chandimal for the 3rd
                        batting position") + theme(axis.title = element_text(size = 15),axis.text = 
                        element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_LD_P_3 <- ggforest(cox_LD_P_3_new , data = LD_P_3,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_LD_P_3
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(cum_balls , wicket) ~ 
                          cum_singles + cum_doubles + cum_boundaries+ridge(cum_dotBalls), data = LD_P_3)
```
\
\
**batting position 4**
\
\
**Filter the first bat_position**
```{r,warning=FALSE,message=FALSE }
LD_P_4<- bt1 %>% filter(bat_position == 4)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
cox_LD_P_4_new <- coxph(Surv(cum_balls , wicket) ~ 
                          cum_singles + cum_doubles + cum_boundaries+ridge(cum_dotBalls), data = LD_P_4)

summary(cox_LD_P_4_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_LD_P_4 <- cox.zph(cox_LD_P_4_new)
test_LD_P_4
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_LD_P_4 <- ggadjustedcurves(cox_LD_P_4_new , data = LD_P_4 , size = 2,
                        ggtheme =theme_survminer()) + geom_hline(yintercept = c(0.25,0.5,0.75) ,
                        linetype = "dashed") +ggtitle("Survival curve for LD Chandimal for the 4th
                        batting position") + theme(axis.title = element_text(size = 15),axis.text = 
                        element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_LD_P_4 <- ggforest(cox_LD_P_4_new , data = LD_P_4,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_LD_P_4
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(cum_balls , wicket) ~ 
                          cum_singles + cum_doubles + cum_boundaries+ridge(cum_dotBalls), data = LD_P_4)
```
\
\
\
\
**5th batting position**
\
\
**Filter the second bat_position**
```{r,warning=FALSE,message=FALSE}
LD_P_5 <- bt1 %>% filter(bat_position == 5)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
cox_LD_P_5_new <- coxph(Surv(cum_balls , wicket) ~ 
                          cum_singles + cum_doubles + cum_boundaries+ridge(cum_dotBalls), data = LD_P_5)
summary(cox_LD_P_5_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_LD_P_5 <- cox.zph(cox_LD_P_5_new)
test_LD_P_5
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_LD_P_5 <- ggadjustedcurves(cox_LD_P_5_new , data = LD_P_5 , size = 2,ggtheme = 
                        theme_survminer()) + geom_hline(yintercept = c(0.25,0.5,0.75) , 
                        linetype = "dashed") +ggtitle("Survival curve for LD Chandimal for 
                        the 5th batting position") + theme(axis.title = element_text(size = 15),
                        axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_LD_P_5 <- ggforest(cox_LD_P_5_new , data = LD_P_5,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_LD_P_5
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(cum_balls , wicket) ~ 
                          cum_singles + cum_doubles + cum_boundaries+ridge(cum_dotBalls), data = LD_P_5)
```
\
\
**Survival curve**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,6)}
LDSurvPlotPos <- ggarrange(cox_plot_LD_P_3,cox_plot_LD_P_4,cox_plot_LD_P_5)
LDSurvPlotPos
```
\
\
**Upload to texStudio**
```{r,results='hide',message=FALSE,warning=FALSE}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"LDSurvPlotPos.eps"),width = 10,height = 7,horizontal = FALSE)
LDSurvPlotPos
dev.off()
```
\
\
**Aalen model**
```{r,warning=FALSE,message=FALSE,fig.dim=c(15,20)}
LD_P_3 <- rename(LD_P_3,cumulative_singles = cum_singles, cumulative_doubles = cum_doubles,cumulative_fours = 
                    cum_boundaries,cumulative_dot_balls=cum_dotBalls)
LD_P_4 <- rename(LD_P_4,cumulative_singles = cum_singles, cumulative_doubles = cum_doubles,cumulative_fours = 
                    cum_boundaries,cumulative_dot_balls=cum_dotBalls)
LD_P_5 <- rename(LD_P_5,cumulative_singles = cum_singles, cumulative_doubles = cum_doubles,cumulative_fours = 
                    cum_boundaries,cumulative_dot_balls=cum_dotBalls)

LD_p3 <- autoplot(aareg(Surv(cum_balls , wicket) ~ 
                          cumulative_singles + cumulative_doubles + cumulative_fours+ridge(cumulative_dot_balls), data = LD_P_3)) +
  theme(legend.position = "none") + ggtitle("Aalen plot of LD Chandimal for 3rd batting position")

LD_p4 <- autoplot(aareg(Surv(cum_balls , wicket) ~ 
                          cumulative_singles + cumulative_doubles + cumulative_fours+ridge(cumulative_dot_balls), data = LD_P_4)) +
  theme(legend.position = "none") + ggtitle("Aalen plot of LD Chandimal 4th batting position")

LD_p5 <- autoplot(aareg(Surv(cum_balls , wicket) ~ 
                          cumulative_singles + cumulative_doubles + cumulative_fours+ridge(cumulative_dot_balls), data = LD_P_5)) +
  theme(legend.position = "none") + ggtitle("Aalen plot of LD Chandimal 5th batting position")

LDAalenPos <- ggarrange(LD_p3,LD_p4,LD_p5, nrow = 3)
LDAalenPos
```

```{r,warning=FALSE,message=FALSE,results='hide'}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"LDAalenPos.eps"),width = 10,height = 20,horizontal = FALSE)
LDAalenPos
dev.off()
```