---
title: "AUC_WUT_INN"
author: "S_16_373"
date: "3/29/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Load the libraries**
```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(survival)
library(ggfortify)
library(survminer)
library(rms)
library(dynpred)
library(MASS)
library(CPE)
library(scatterplot3d)
library(plotly)
```
\
\
**Read the data sets**
```{r,warning=FALSE,message=FALSE}
Home <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Home/Home.csv")
Overseas <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Overseas/Overseas.csv")
```
\
\
**Merge two data sets**
```{r,warning=FALSE,message=FALSE}
data_merge <- rbind(Home , Overseas)
```
\
\
**Filter the data of WU Tharanga**
```{r,warning=FALSE,message=FALSE}
bt15 <- data_merge %>% filter(grepl('WU Tharanga' , Striker))
```
\
\
***1)Analysis for two different innings***
\
\
**First innings**
\
\
**Filter the first innings**
```{r,warning=FALSE,message=FALSE}
WUT_1 <- bt15 %>% filter(innings == 1)
```
\
\
**Cox model for first innings**
```{r,warning=FALSE,message=FALSE}
cox_WUT_1 <- coxph(Surv(cum_balls , wicket) ~ 
                     cum_runs+cum_singles+cum_doubles+cum_boundaries+ridge(cum_dotBalls), data = WUT_1)
summary(cox_WUT_1)
```
\
\
**Finding the best model using AIC**
```{r,warning=FALSE,message=FALSE}
model_WUT_1 <- stepAIC(cox_WUT_1)
```
\
\
**Best Model**
```{r,warning=FALSE,message=FALSE}
cox_WUT_1_new <- coxph(Surv(cum_balls , wicket) ~ 
                         cum_runs + cum_singles + cum_boundaries+ ridge(cum_dotBalls), data = WUT_1)
summary(cox_WUT_1_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_WUT_1 <- cox.zph(cox_WUT_1_new)
test_WUT_1
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_WUT_1 <- ggadjustedcurves(cox_WUT_1_new , data = WUT_1 , size = 2,ggtheme = theme_survminer()) + 
                  geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +xlim(0,80) +
                    ggtitle("Survival curve for WU Tharanga for the first innings") + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))

cox_plot_WUT_1
```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE}
coef_plot_WUT_1 <- ggforest(cox_WUT_1_new , data = WUT_1,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_WUT_1
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(cum_balls , wicket) ~ 
      cum_runs + cum_singles + cum_boundaries+ ridge(cum_dotBalls), data = WUT_1)
```
\
\
**percentage of matches won when the player is in the specific match**
```{r,warning=FALSE,message=FALSE}
match_status_WUT_1 <- unique(WUT_1[c("Match_Number","winning_status")])
tot_matches_WUT_1 <- nrow(match_status_WUT_1)
win_matches_WUT_1 <- sum(match_status_WUT_1$winning_status==1)

win_percent_WUT_1 <- (win_matches_WUT_1/tot_matches_WUT_1)*100

win_percent_WUT_1
```
\
\
**Runs contributed**
```{r,warning=FALSE,message=FALSE}
match_played_WUT_1 <- data_merge %>% filter(Match_Number %in% unique(WUT_1$Match_Number))
tot_runs_WUT_1 <- match_played_WUT_1 %>% summarise(sum_runs = sum(tot_runs))
WUT_runs_1 <- WUT_1 %>%  summarise(sum_runs = sum(tot_runs))

runs_contrib_percent_WUT_1 <- (WUT_runs_1/tot_runs_WUT_1)*100
runs_contrib_percent_WUT_1
```
\
\
**Second Innings**
\
\
**Filter the second innings**
```{r,warning=FALSE,message=FALSE}
WUT_2 <- bt15 %>% filter(innings == 2)
```
\
\
**Cox model for second innings**
```{r,warning=FALSE,message=FALSE}
cox_WUT_2 <- coxph(Surv(cum_balls , wicket) ~ 
                     cum_runs+cum_singles+cum_doubles+cum_boundaries+ridge(cum_dotBalls), data = WUT_2)
summary(cox_WUT_2)
```
\
\
**Finding the best model using AIC**
```{r,warning=FALSE,message=FALSE}
model_WUT_2 <- stepAIC(cox_WUT_2)
```
\
\
**Best Model**
```{r,warning=FALSE,message=FALSE}
cox_WUT_2_new <- coxph(Surv(cum_balls , wicket) ~ 
                         cum_runs + cum_singles+ ridge(cum_dotBalls), data = WUT_2)
summary(cox_WUT_2_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_WUT_2 <- cox.zph(cox_WUT_2_new)
test_WUT_2
```
\
\
**Extended cox model**
```{r,warning=FALSE,message=FALSE}
WUT_2_cut <- survSplit(WUT_2 , cut = 50 , end = "cum_balls" , event = "wicket" , start = "start" , id = "id")

WUT_2_cut$hv1 <- WUT_2_cut$cum_runs  * (WUT_2_cut$start < 50)
WUT_2_cut$hv2 <- WUT_2_cut$cum_runs  * (WUT_2_cut$start >= 50)

WUT_2_cut$hv3 <- WUT_2_cut$cum_singles   * (WUT_2_cut$start < 50)
WUT_2_cut$hv4 <- WUT_2_cut$cum_singles   * (WUT_2_cut$start >= 50)

cox_WUT_2_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                     hv1 + hv2 +hv3 +hv4 + ridge(cum_dotBalls) + cluster (id) , data = WUT_2_cut)
summary(cox_WUT_2_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_WUT_2_heav <- cox.zph(cox_WUT_2_heav)
test_WUT_2_heav
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_WUT_2 <- ggadjustedcurves(cox_WUT_2_heav , data = WUT_2_cut , size = 2,ggtheme = theme_survminer()) + 
                  geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed")  +
                    ggtitle("Survival curve for WU Tharanga for the second innings") +
                    theme(text = element_text(size = 20))

cox_plot_WUT_2
```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE}
coef_plot_WUT_2 <- ggforest(cox_WUT_2_heav , data = WUT_2_cut,fontsize = 1.2)
coef_plot_WUT_2
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
                     hv1 + hv2 +hv3 +hv4 + ridge(cum_dotBalls) + cluster (id) , data = WUT_2_cut)
```
\
\
**percentage of matches won when the player is in the specific match**
```{r,warning=FALSE,message=FALSE}
match_status_WUT_2 <- unique(WUT_2[c("Match_Number","winning_status")])
tot_matches_WUT_2 <- nrow(match_status_WUT_2)
win_matches_WUT_2 <- sum(match_status_WUT_2$winning_status==1)

win_percent_WUT_2 <- (win_matches_WUT_2/tot_matches_WUT_2)*100

win_percent_WUT_2
```
\
\
**Runs contributed**
```{r,warning=FALSE,message=FALSE}
match_played_WUT_2 <- data_merge %>% filter(Match_Number %in% unique(WUT_2$Match_Number))
tot_runs_WUT_2 <- match_played_WUT_2 %>% summarise(sum_runs = sum(tot_runs))
WUT_runs_2 <- WUT_2 %>%  summarise(sum_runs = sum(tot_runs))

runs_contrib_percent_WUT_2 <- (WUT_runs_2/tot_runs_WUT_2)*100
runs_contrib_percent_WUT_2
```
\
\
\
***Compare different innings***
\
\
**Create the data frame**
```{r,warning=FALSE,message=FALSE}
PlayerName_WUT <- "WU Tharanga"
Innings <- c(1,2)
Survival_prob_WUT <- c(0.95671,0.9727967)
winning_percent_WUT <- c(21.42857,27.27273)
runs_contrib_percent_WUT <- c(11.92701 ,18.88664)

comp_innings_WUT <- data.frame(PlayerName_WUT,Innings,Survival_prob_WUT,runs_contrib_percent_WUT,winning_percent_WUT)
names(comp_innings_WUT) <- c("PlayerName","Innings","Survival_prob","runs_contrib_percent","winning_percent")
comp_innings_WUT
```
\
\