---
title: "WUT_POS"
author: "S_16_373"
date: "5/17/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


**Load the libraries**
```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(survival)
library(ggfortify)
library(survminer)
library(rms)
library(dynpred)
library(MASS)
library(CPE)
library(scatterplot3d)
library(plotly)
```
\
\
**Read the data sets**
```{r,warning=FALSE,message=FALSE}
Home <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Home/Home.csv")
Overseas <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Overseas/Overseas.csv")
```
\
\
**Merge two data sets**
```{r,warning=FALSE,message=FALSE}
data_merge <- rbind(Home , Overseas)
```
\
\
**Filter the data of WU Tharanga**
```{r,warning=FALSE,message=FALSE}
bt15 <- data_merge %>% filter(grepl('WU Tharanga' , Striker))
```
\
\
***1)Analysis for different batting position***
\
\
```{r,message=FALSE,warning=FALSE}
bt15_ps <- bt15 %>% filter(bat_position == c(2,4))

WUT_diff_pos <- survdiff(Surv(cum_balls , wicket) ~ bat_position, data = bt15_ps)
WUT_diff_pos
```
The p value is greater than 0.05. Therefore no significant difference between the batting positions 2 and 4.

\
\
**batting position 2**
\
\
**Filter the first bat_position**
```{r,warning=FALSE,message=FALSE}
WUT_P_2<- bt15 %>% filter(bat_position == 2)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
WUT_P_2_cut <- survSplit(WUT_P_2 , cut = 50 , end = "cum_balls" , event = "wicket" , start = "start" , id = "id")


WUT_P_2_cut$hv1 <- WUT_P_2_cut$cum_singles   * (WUT_P_2_cut$start < 50)
WUT_P_2_cut$hv2 <- WUT_P_2_cut$cum_singles   * (WUT_P_2_cut$start >= 50)

cox_WUT_P_2_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                             hv1 + hv2+ cum_doubles + cum_boundaries+ cluster (id) , data = WUT_P_2_cut)

summary(cox_WUT_P_2_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_WUT_P_2 <- cox.zph(cox_WUT_P_2_heav)
test_WUT_P_2
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_WUT_P_2 <- ggadjustedcurves(cox_WUT_P_2_heav , data = WUT_P_2_cut , size = 2,
                        ggtheme =theme_survminer()) + geom_hline(yintercept = c(0.25,0.5,0.75) ,
                        linetype = "dashed") +ggtitle("Survival curve for WU Tharanga for the 2nd
                        batting position") + theme(axis.title = element_text(size = 15),axis.text = 
                        element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_WUT_P_2 <- ggforest(cox_WUT_P_2_heav , data = WUT_P_2_cut,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_WUT_P_2
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
                             hv1 + hv2+ cum_doubles + cum_boundaries+ cluster (id) , data = WUT_P_2_cut)
```
\
\
**4th batting position**
\
\
**Filter the second bat_position**
```{r,warning=FALSE,message=FALSE}
WUT_P_4 <- bt15 %>% filter(bat_position == 4)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
WUT_P_4_cut <- survSplit(WUT_P_4 , cut = 50 , end = "cum_balls" , event = "wicket" , start = "start" , id = "id")

WUT_P_4_cut$hv1 <- WUT_P_4_cut$cum_singles   * (WUT_P_4_cut$start < 50)
WUT_P_4_cut$hv2 <- WUT_P_4_cut$cum_singles   * (WUT_P_4_cut$start >= 50)

cox_WUT_P_4_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                            hv1 + hv2+ cum_doubles + cum_boundaries + cluster (id) , data = WUT_P_4_cut)


summary(cox_WUT_P_4_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_WUT_P_4 <- cox.zph(cox_WUT_P_4_heav)
test_WUT_P_4
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_WUT_P_4 <- ggadjustedcurves(cox_WUT_P_4_heav , data = WUT_P_4_cut , size = 2,ggtheme = 
                        theme_survminer()) + geom_hline(yintercept = c(0.25,0.5,0.75) , 
                        linetype = "dashed") +ggtitle("Survival curve for WU Tharanga for 
                        the 4th batting position") + theme(axis.title = element_text(size = 15),
                        axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_WUT_P_4 <- ggforest(cox_WUT_P_4_heav , data = WUT_P_4_cut,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_WUT_P_4
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
                            hv1 + hv2+ cum_doubles + cum_boundaries + cluster (id) , data = WUT_P_4_cut)
```
\
\
**Survival curve**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,6)}
WUTSurvPlotPos <- ggarrange(cox_plot_WUT_P_2,cox_plot_WUT_P_4,ncol = 2)
WUTSurvPlotPos
```
\
\
**Upload to texStudio**
```{r,results='hide',message=FALSE,warning=FALSE}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"WUTSurvPlotPos.eps"),width = 10,height = 7,horizontal = FALSE)
WUTSurvPlotPos
dev.off()
```
\
\
**Aalen model**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,7)}
WUT_P_2_cut <- rename(WUT_P_2_cut,cumulative_singles_lt50 = hv1, cumulative_singles_ge50 = hv2 ,cumulative_doubles = 
                      cum_doubles,cumulative_fours = cum_boundaries,cumulative_dot_balls=cum_dotBalls)
WUT_P_4_cut <- rename(WUT_P_4_cut,cumulative_singles_lt50 = hv1, cumulative_singles_ge50 = hv2,cumulative_doubles = 
                      cum_doubles,cumulative_fours = cum_boundaries,cumulative_dot_balls=cum_dotBalls)


WUT_p_2 <- autoplot(aareg(Surv(start,cum_balls , wicket) ~ 
                            cumulative_singles_lt50 + cumulative_singles_ge50+ cumulative_doubles + cumulative_fours + 
                            cluster (id) , data = WUT_P_2_cut)) +theme(legend.position = "none") + 
  ggtitle("Aalen plot of WU Tharanga for the 2nd batting position")

WUT_p_4 <- autoplot(aareg(Surv(start,cum_balls , wicket) ~ 
                            cumulative_singles_lt50 + cumulative_singles_ge50+ cumulative_doubles + cumulative_fours + 
                            cluster (id) , data = WUT_P_4_cut)) +theme(legend.position = "none") + 
  ggtitle("Aalen plot of WU Tharanga for the 4th batting position")

WUTAalenPos <- ggarrange(WUT_p_2,WUT_p_4, nrow = 2)
WUTAalenPos
```

```{r,warning=FALSE,message=FALSE,results='hide'}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"WUTAalenPos.eps"),width = 10,height = 7,horizontal = FALSE)
WUTAalenPos
dev.off()
```

