---
title: "WUT_VEN"
author: "S_16_373"
date: "5/17/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


**Load the libraries**
```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(survival)
library(ggfortify)
library(survminer)
library(rms)
library(dynpred)
library(MASS)
library(CPE)
library(scatterplot3d)
library(plotly)
```
\
\
**Read the data sets**
```{r,warning=FALSE,message=FALSE}
Home <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Home/Home.csv")
Overseas <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Overseas/Overseas.csv")
```
\
\
**Merge two data sets**
```{r,warning=FALSE,message=FALSE}
data_merge <- rbind(Home , Overseas)
```
\
\
**Filter the data of WU Tharanga**
```{r,warning=FALSE,message=FALSE}
bt15 <- data_merge %>% filter(grepl('WU Tharanga' , Striker))
```
\
\
***1)Analysis for two different Venue***
\
\
```{r,message=FALSE,warning=FALSE}
WUT_diff_ven <- survdiff(Surv(cum_balls , wicket) ~ Venue, data = bt15)
WUT_diff_ven
```
The p value is less than 0.05. Therefore we can see a significant difference between the Venue.

\
\
**Home**
\
\
**Filter the first Venue**
```{r,warning=FALSE,message=FALSE}
WUT_H <- bt15 %>% filter(Venue == "Home")
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
cox_WUT_H_new <- coxph(Surv(cum_balls , wicket) ~ 
                         cum_doubles+cum_boundaries+ ridge(cum_dotBalls), data = WUT_H)

summary(cox_WUT_H_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_WUT_H <- cox.zph(cox_WUT_H_new)
test_WUT_H
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_WUT_H <- ggadjustedcurves(cox_WUT_H_new , data = WUT_H , size = 2,
                          ggtheme = theme_survminer()) + 
                          geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +
                          ggtitle("Survival curve for WU Tharanga for Venue Home") + 
                          theme(axis.title = element_text(size = 15),
                                axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_WUT_H <- ggforest(cox_WUT_H_new , data = WUT_H,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_WUT_H
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(cum_balls , wicket) ~ 
                         cum_doubles+cum_boundaries+ ridge(cum_dotBalls), data = WUT_H)
```
\
\
**Second Venue**
\
\
**Filter the second Venue**
```{r,warning=FALSE,message=FALSE}
WUT_O <- bt15 %>% filter(Venue == "Overseas")
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
cox_WUT_O_new <- coxph(Surv(cum_balls , wicket) ~ 
                         cum_doubles+cum_boundaries+ ridge(cum_dotBalls), data = WUT_O)

summary(cox_WUT_O_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_WUT_O <- cox.zph(cox_WUT_O_new)
test_WUT_O
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_WUT_O <- ggadjustedcurves(cox_WUT_O_new , data = WUT_O , size = 2,
                          ggtheme = theme_survminer()) + 
                          geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +
                          ggtitle("Survival curve for WU Tharanga for Venue Overseas") + 
                          theme(axis.title = element_text(size = 15),
                                axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_WUT_O <- ggforest(cox_WUT_O_new , data = WUT_O,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_WUT_O
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(cum_balls , wicket) ~ 
                         cum_doubles+cum_boundaries+ ridge(cum_dotBalls), data = WUT_O)
```
\
\
**Survival curve**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,6)}
WUTSurvPlotVen <- ggarrange(cox_plot_WUT_H,cox_plot_WUT_O,ncol = 2)
WUTSurvPlotVen
```
\
\
**Upload to texStudio**
```{r,results='hide',message=FALSE,warning=FALSE}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"WUTSurvPlotVen.eps"),width = 10,height = 7,horizontal = FALSE)
WUTSurvPlotVen
dev.off()
```
\
\
**Aalen model**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,7)}
WUT_H <- rename(WUT_H, cumulative_doubles = cum_doubles,cumulative_fours = cum_boundaries,cumulative_dot_balls=cum_dotBalls)
WUT_O <- rename(WUT_O,cumulative_doubles = cum_doubles,cumulative_fours = cum_boundaries,cumulative_dot_balls=cum_dotBalls)

WUT_pH <- autoplot(aareg(Surv(cum_balls , wicket) ~ 
                         cumulative_doubles+cumulative_fours+ ridge(cumulative_dot_balls), data = WUT_H)) +
  theme(legend.position = "none") + ggtitle("Aalen plot of WU Tharanga for home venue")

WUT_pO <- autoplot(aareg(Surv(cum_balls , wicket) ~ 
                         cumulative_doubles+cumulative_fours+ ridge(cumulative_dot_balls), data = WUT_O)) +
  theme(legend.position = "none") + ggtitle("Aalen plot of WU Tharanga for overseas venue")

WUTAalenVen <- ggarrange(WUT_pH,WUT_pO, nrow = 2)
WUTAalenVen
```

```{r,warning=FALSE,message=FALSE,results='hide'}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"WUTAalenVen.eps"),width = 10,height = 7,horizontal = FALSE)
WUTAalenVen
dev.off()
```
