---
title: "ADM_POS"
author: "S_16_373"
date: "5/8/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Load the libraries**
```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(survival)
library(ggfortify)
library(survminer)
library(rms)
library(dynpred)
library(MASS)
library(CPE)
library(scatterplot3d)
library(plotly)
```
\
\
**Read the data sets**
```{r,warning=FALSE,message=FALSE}
Home <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Home/Home.csv")
Overseas <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Overseas/Overseas.csv")
```
\
\
**Merge two data sets**
```{r,warning=FALSE,message=FALSE}
data_merge <- rbind(Home , Overseas)
```
\
\
**Filter the data of AD Mathews**
```{r,warning=FALSE,message=FALSE}
bt2 <- data_merge %>% filter(grepl('AD Mathews' , Striker))
```
\
\
***1)Analysis for different batting position***
\
\
```{r,message=FALSE,warning=FALSE}
bt2_ps <- bt2 %>% filter(bat_position == c(4,5))

ADM_diff_pos <- survdiff(Surv(cum_balls , wicket) ~ bat_position, data = bt2_ps)
ADM_diff_pos
```
The p value is greater than 0.05. Therefore we cannot see a significant difference between the batting positions 4 and 5.

\
\
**batting position 4**
\
\
**Filter the first bat_position**
```{r,warning=FALSE,message=FALSE}
ADM_P_4<- bt2 %>% filter(bat_position == 4)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
cox_ADM_P_4_new <- coxph(Surv(cum_balls , wicket) ~ 
                         cum_doubles+cum_boundaries+ridge(cum_dotBalls), data = ADM_P_4)

summary(cox_ADM_P_4_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_ADM_P_4 <- cox.zph(cox_ADM_P_4_new)
test_ADM_P_4
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_ADM_P_4 <- ggadjustedcurves(cox_ADM_P_4_new , data = ADM_P_4 , size = 2,
                        ggtheme =theme_survminer()) + geom_hline(yintercept = c(0.25,0.5,0.75) ,
                        linetype = "dashed") +ggtitle("Survival curve for AD Mathews for the 4th
                        batting position") + theme(axis.title = element_text(size = 15),axis.text = 
                        element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_ADM_P_4 <- ggforest(cox_ADM_P_4_new , data = ADM_P_4,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_ADM_P_4
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(cum_balls , wicket) ~ 
                         cum_doubles+cum_boundaries+ridge(cum_dotBalls), data = ADM_P_4)
```
\
\
**5th batting position**
\
\
**Filter the second bat_position**
```{r,warning=FALSE,message=FALSE}
ADM_P_5 <- bt2 %>% filter(bat_position == 5)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
cox_ADM_P_5_new <- coxph(Surv(cum_balls , wicket) ~ 
                        cum_doubles+cum_boundaries+ridge(cum_dotBalls), data = ADM_P_5)
summary(cox_ADM_P_5_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_ADM_P_5 <- cox.zph(cox_ADM_P_5_new)
test_ADM_P_5
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_ADM_P_5 <- ggadjustedcurves(cox_ADM_P_5_new , data = ADM_P_5 , size = 2,ggtheme = 
                        theme_survminer()) + geom_hline(yintercept = c(0.25,0.5,0.75) , 
                        linetype = "dashed") +ggtitle("Survival curve for AD Mathews for 
                        the 5th batting position") + theme(axis.title = element_text(size = 15),
                        axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_ADM_P_5 <- ggforest(cox_ADM_P_5_new , data = ADM_P_5,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_ADM_P_5
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(cum_balls , wicket) ~ 
                        cum_doubles+cum_boundaries+ridge(cum_dotBalls), data = ADM_P_5)
```
\
\
**Survival curve**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,6)}
ADMSurvPlotPos <- ggarrange(cox_plot_ADM_P_4,cox_plot_ADM_P_5,ncol = 2)
ADMSurvPlotPos
```
\
\
**Upload to texStudio**
```{r,results='hide',message=FALSE,warning=FALSE}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"ADMSurvPlotPos.eps"),width = 10,height = 7,horizontal = FALSE)
ADMSurvPlotPos
dev.off()
```
\
\
**Aalen model**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,7)}
ADM_P_4 <- rename(ADM_P_4, cumulative_doubles = cum_doubles,cumulative_fours = 
                    cum_boundaries,cumulative_dot_balls=cum_dotBalls)
ADM_P_5 <- rename(ADM_P_5, cumulative_doubles = cum_doubles,cumulative_fours = 
                    cum_boundaries,cumulative_dot_balls=cum_dotBalls)

ADM_p4 <- autoplot(aareg(Surv(cum_balls , wicket) ~ 
                        cumulative_doubles+cumulative_fours+ridge(cumulative_dot_balls), data = ADM_P_4)) + 
  theme(legend.position = "none") + ggtitle("Aalen plot of AD Mathews 4th batting position") 

ADM_p5 <- autoplot(aareg(Surv(cum_balls , wicket) ~ 
                        cumulative_doubles+cumulative_fours+ridge(cumulative_dot_balls), data = ADM_P_5)) + 
  theme(legend.position = "none") + 
  ggtitle("Aalen plot of AD Mathews for 5th batting position") 

ADMAalenPos <- ggarrange(ADM_p4,ADM_p5, nrow = 2)
ADMAalenPos
```

```{r,warning=FALSE,message=FALSE,results='hide'}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"ADMAalenPos.eps"),width = 10,height = 7,horizontal = FALSE)
ADMAalenPos
dev.off()
```

