---
title: "ADM_VEN"
author: "S_16_373"
date: "5/8/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Load the libraries**
```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(survival)
library(ggfortify)
library(survminer)
library(rms)
library(dynpred)
library(MASS)
library(CPE)
library(scatterplot3d)
library(plotly)
```
\
\
**Read the data sets**
```{r,warning=FALSE,message=FALSE}
Home <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Home/Home.csv")
Overseas <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Overseas/Overseas.csv")
```
\
\
**Merge two data sets**
```{r,warning=FALSE,message=FALSE}
data_merge <- rbind(Home , Overseas)
```
\
\
**Filter the data of AD Mathews**
```{r,warning=FALSE,message=FALSE}
bt2 <- data_merge %>% filter(grepl('AD Mathews' , Striker))
```
\
\
***1)Analysis for two different Venue***
\
\
```{r,message=FALSE,warning=FALSE}
ADM_diff_ven <- survdiff(Surv(cum_balls , wicket) ~ Venue, data = bt2)
ADM_diff_ven
```
The p value is greater than 0.05. Therefore we cannot see a significant difference between the Venue.

\
\
**Home**
\
\
**Filter the first Venue**
```{r,warning=FALSE,message=FALSE}
ADM_H <- bt2 %>% filter(Venue == "Home")
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
cox_ADM_H_new <- coxph(Surv(cum_balls , wicket) ~ 
                         cum_runs  +cum_boundaries+ ridge(cum_dotBalls), data = ADM_H)

summary(cox_ADM_H_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_ADM_H <- cox.zph(cox_ADM_H_new)
test_ADM_H
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_ADM_H <- ggadjustedcurves(cox_ADM_H_new , data = ADM_H , size = 2,
                          ggtheme = theme_survminer()) + 
                          geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +
                          ggtitle("Survival curve for AD Mathews for Venue Home") + 
                          theme(axis.title = element_text(size = 15),
                                axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_ADM_H <- ggforest(cox_ADM_H_new , data = ADM_H,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_ADM_H
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(cum_balls , wicket) ~ 
                         cum_runs  +cum_boundaries+ ridge(cum_dotBalls), data = ADM_H)
```
\
\
**Second Venue**
\
\
**Filter the second Venue**
```{r,warning=FALSE,message=FALSE}
ADM_O <- bt2 %>% filter(Venue == "Overseas")
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
cox_ADM_O_new <- coxph(Surv(cum_balls , wicket) ~ 
                         cum_runs  +cum_boundaries+ ridge(cum_dotBalls), data = ADM_O)
summary(cox_ADM_O_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_ADM_O <- cox.zph(cox_ADM_O_new)
test_ADM_O
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_ADM_O <- ggadjustedcurves(cox_ADM_O_new , data = ADM_O , size = 2,
                          ggtheme = theme_survminer()) + 
                          geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +
                          ggtitle("Survival curve for AD Mathews for Venue Overseas") + 
                          theme(axis.title = element_text(size = 15),
                                axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_ADM_O <- ggforest(cox_ADM_O_new , data = ADM_O,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_ADM_O
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(cum_balls , wicket) ~ 
                         cum_runs  +cum_boundaries+ ridge(cum_dotBalls), data = ADM_O)
```
\
\
**Survival curve**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,6)}
ADMSurvPlotVen <- ggarrange(cox_plot_ADM_H,cox_plot_ADM_O,ncol = 2)
ADMSurvPlotVen
```
\
\
**Upload to texStudio**
```{r,results='hide',message=FALSE,warning=FALSE}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"ADMSurvPlotVen.eps"),width = 10,height = 7,horizontal = FALSE)
ADMSurvPlotVen
dev.off()
```
\
\
**Aalen model**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,7)}
ADM_H <- rename(ADM_H, cumulative_runs = cum_runs,cumulative_fours = cum_boundaries,cumulative_dot_balls=cum_dotBalls)
ADM_O <- rename(ADM_O, cumulative_runs = cum_runs,cumulative_fours = cum_boundaries,cumulative_dot_balls=cum_dotBalls)

ADM_pH <- autoplot(aareg(Surv(cum_balls , wicket) ~ 
                         cumulative_runs  +cumulative_fours+ ridge(cumulative_dot_balls), data = ADM_H)) +
  theme(legend.position = "none") + ggtitle("Aalen plot of AD Mathews for home venue")

ADM_pO <- autoplot(aareg(Surv(cum_balls , wicket) ~ 
                         cumulative_runs  +cumulative_fours+ ridge(cumulative_dot_balls), data = ADM_O)) +
  theme(legend.position = "none") + ggtitle("Aalen plot of AD Mathews for overseas venue")

ADMAalenVen <- ggarrange(ADM_pH,ADM_pO, nrow = 2)
ADMAalenVen
```

```{r,warning=FALSE,message=FALSE,results='hide'}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"ADMAalenVen.eps"),width = 10,height = 7,horizontal = FALSE)
ADMAalenVen
dev.off()
```