---
title: "ADM_INN"
author: "S_16_373"
date: "5/8/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Load the libraries**
```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(survival)
library(ggfortify)
library(survminer)
library(rms)
library(dynpred)
library(MASS)
library(CPE)
library(scatterplot3d)
library(plotly)
```
\
\
**Read the data sets**
```{r,warning=FALSE,message=FALSE}
Home <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Home/Home.csv")
Overseas <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Overseas/Overseas.csv")
```
\
\
**Merge two data sets**
```{r,warning=FALSE,message=FALSE}
data_merge <- rbind(Home , Overseas)
```
\
\
**Filter the data of AD Mathews**
```{r,warning=FALSE,message=FALSE}
bt2 <- data_merge %>% filter(grepl('AD Mathews' , Striker))
```
\
\
***1)Analysis for two different innings***
\
\
```{r,message=FALSE,warning=FALSE}
ADM_diff_inn <- survdiff(Surv(cum_balls , wicket) ~ innings, data = bt2)
ADM_diff_inn
```
The p value is greater than 0.05. Therefore we cannot see a significant difference between the innings.

\
\
**First innings**
\
\
**Filter the first innings**
```{r,warning=FALSE,message=FALSE}
ADM_1 <- bt2 %>% filter(innings == 1)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
cox_ADM_1_new <- coxph(Surv(cum_balls , wicket) ~ 
                         cum_runs +  ridge(cum_dotBalls), data = ADM_1)

summary(cox_ADM_1_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_ADM_1 <- cox.zph(cox_ADM_1_new)
test_ADM_1
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_ADM_1 <- ggadjustedcurves(cox_ADM_1_new , data = ADM_1 , size = 2,
                      ggtheme = theme_survminer()) + 
                      geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +
                      ggtitle("Survival curve for AD Mathews for the first innings") + 
                      theme(axis.title = element_text(size = 15),
                            axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_ADM_1 <- ggforest(cox_ADM_1_new , data = ADM_1,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_ADM_1
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(cum_balls , wicket) ~ 
                         cum_runs +  ridge(cum_dotBalls), data = ADM_1)
```
\
\
**Second Innings**
\
\
**Filter the second innings**
```{r,warning=FALSE,message=FALSE}
ADM_2 <- bt2 %>% filter(innings == 2)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
cox_ADM_2_new <- coxph(Surv(cum_balls , wicket) ~ 
                         cum_runs +  ridge(cum_dotBalls), data = ADM_2)

summary(cox_ADM_2_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_ADM_2 <- cox.zph(cox_ADM_2_new)
test_ADM_2
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_ADM_2 <- ggadjustedcurves(cox_ADM_2_new , data = ADM_2 , size = 2,
                        ggtheme = theme_survminer()) + 
                        geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +
                        ggtitle("Survival curve for AD Mathews for the second innings") + 
                        theme(axis.title = element_text(size = 15),
                              axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_ADM_2 <- ggforest(cox_ADM_2_new , data = ADM_2,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_ADM_2
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(cum_balls , wicket) ~ 
                         cum_runs +  ridge(cum_dotBalls), data = ADM_2)
```
\
\
**Survival curve**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,6)}
ADMSurvPlotInn <- ggarrange(cox_plot_ADM_1,cox_plot_ADM_2,ncol = 2)
ADMSurvPlotInn
```
\
\
**Upload to texStudio**
```{r,results='hide',message=FALSE,warning=FALSE}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"ADMSurvPlotInn.eps"),width = 10,height = 7,horizontal = FALSE)
ADMSurvPlotInn
dev.off()
```
\
\
**Aalen model**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,7)}

ADM_1 <- rename(ADM_1, cumulative_runs = cum_runs,cumulative_dot_balls=cum_dotBalls)
ADM_2 <- rename(ADM_2, cumulative_runs = cum_runs,cumulative_dot_balls=cum_dotBalls)

ADM_p1 <- autoplot(aareg(Surv(cum_balls , wicket) ~ 
                         cumulative_runs +  ridge(cumulative_dot_balls), data = ADM_1)) + theme(legend.position = "none") + 
  ggtitle("Aalen plot of AD Mathews for first innings") 

ADM_p2 <- autoplot(aareg(Surv(cum_balls , wicket) ~ 
                         cumulative_runs +  ridge(cumulative_dot_balls), data = ADM_2)) + theme(legend.position = "none") +  
  ggtitle("Aalen plot of AD Mathews for second innings")

ADMAalenInn <- ggarrange(ADM_p1,ADM_p2, nrow = 2)
ADMAalenInn
```

```{r,warning=FALSE,message=FALSE,results='hide'}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"ADMAalenInn.eps"),width = 10,height = 7,horizontal = FALSE)
ADMAalenInn
dev.off()
```

