---
title: "MDG_INN"
author: "S_16_373"
date: "5/8/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Load the libraries**
```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(survival)
library(ggfortify)
library(survminer)
library(rms)
library(dynpred)
library(MASS)
library(CPE)
library(scatterplot3d)
library(plotly)
```
\
\
**Read the data sets**
```{r,warning=FALSE,message=FALSE}
Home <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Home/Home.csv")
Overseas <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Overseas/Overseas.csv")
```
\
\
**Merge two data sets**
```{r,warning=FALSE,message=FALSE}
data_merge <- rbind(Home , Overseas)
```
\
\
**Filter the data of MD Gunathilaka**
```{r,warning=FALSE,message=FALSE}
bt4<- data_merge %>% filter(grepl('MD Gunathilaka' , Striker))
```
\
\
***1)Analysis for two different innings***
\
\
```{r,message=FALSE,warning=FALSE}
MDG_diff_inn <- survdiff(Surv(cum_balls , wicket) ~ innings, data = bt4)
MDG_diff_inn
```
The p value is greater than 0.05. Therefore no significant difference between the innings.

\
\
**First innings**
\
\
**Filter the first innings**
```{r,warning=FALSE,message=FALSE}
MDG_1 <- bt4%>% filter(innings == 1)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
MDG_1_cut <- survSplit(MDG_1 , cut = 38 , end = "cum_balls" , event = "wicket" , start = "start" , id = "id")

MDG_1_cut$hv1 <- MDG_1_cut$cum_singles * (MDG_1_cut$start < 38)
MDG_1_cut$hv2 <- MDG_1_cut$cum_singles * (MDG_1_cut$start >= 38)


cox_MDG_1_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                         hv1 + hv2 +  ridge(cum_dotBalls) + cluster (id) , data = MDG_1_cut)


summary(cox_MDG_1_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_MDG_1 <- cox.zph(cox_MDG_1_heav)
test_MDG_1
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_MDG_1 <- ggadjustedcurves(cox_MDG_1_heav , data = MDG_1_cut , size = 2,
                      ggtheme = theme_survminer()) + 
                      geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +
                      ggtitle("Survival curve for MD Gunathilaka for the first innings") + 
                      theme(axis.title = element_text(size = 15),
                            axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_MDG_1 <- ggforest(cox_MDG_1_heav , data = MDG_1_cut,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_MDG_1
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
                         hv1 + hv2 +  ridge(cum_dotBalls) + cluster (id) , data = MDG_1_cut)
```
\
\
**Second Innings**
\
\
**Filter the second innings**
```{r,warning=FALSE,message=FALSE}
MDG_2 <- bt4%>% filter(innings == 2)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
MDG_2_cut <- survSplit(MDG_2 , cut = 38 , end = "cum_balls" , event = "wicket" , start = "start" , id = "id")

MDG_2_cut$hv1 <- MDG_2_cut$cum_singles * (MDG_2_cut$start < 38)
MDG_2_cut$hv2 <- MDG_2_cut$cum_singles * (MDG_2_cut$start >= 38)


cox_MDG_2_heav <- coxph(Surv(start,cum_balls , wicket) ~ 
                          hv1 + hv2  + ridge(cum_dotBalls) + cluster (id) , data = MDG_2_cut)
summary(cox_MDG_2_heav)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_MDG_2 <- cox.zph(cox_MDG_2_heav)
test_MDG_2
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_MDG_2 <- ggadjustedcurves(cox_MDG_2_heav , data = MDG_2_cut , size = 2,
                        ggtheme = theme_survminer()) + 
                        geom_hline(yintercept = c(0.25,0.5,0.75) , linetype = "dashed") +
                        ggtitle("Survival curve for MD Gunathilaka for the second innings") + 
                        theme(axis.title = element_text(size = 15),
                              axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_MDG_2 <- ggforest(cox_MDG_2_heav , data = MDG_2_cut,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_MDG_2
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(start,cum_balls , wicket) ~ 
                         hv1 + hv2 +  ridge(cum_dotBalls) + cluster (id) , data = MDG_2_cut)
```
\
\
**Survival curve**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,6)}
MDGSurvPlotInn <- ggarrange(cox_plot_MDG_1,cox_plot_MDG_2,ncol = 2)
MDGSurvPlotInn
```
\
\
**Upload to texStudio**
```{r,results='hide',message=FALSE,warning=FALSE}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"MDGSurvPlotInn.eps"),width = 10,height = 7,horizontal = FALSE)
MDGSurvPlotInn
dev.off()
```
\
\
**Aalen model**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,7)}
MDG_1_cut <- rename(MDG_1_cut,cumulative_singles_lt38 = hv1, cumulative_singles_ge38 = hv2 ,cumulative_dot_balls=cum_dotBalls)
MDG_2_cut <- rename(MDG_2_cut,cumulative_singles_lt38 = hv1, cumulative_singles_ge38 = hv2,cumulative_dot_balls=cum_dotBalls)

MDG_p1 <- autoplot(aareg(Surv(start,cum_balls , wicket) ~ 
                         cumulative_singles_lt38 + cumulative_singles_ge38 +  ridge(cumulative_dot_balls) + cluster (id) , data = MDG_1_cut))+ theme(legend.position = "none") + 
  ggtitle("Aalen plot of MD Gunathilaka for the first innings") 

MDG_p2 <- autoplot(aareg(Surv(start,cum_balls , wicket) ~ 
                         cumulative_singles_lt38 + cumulative_singles_ge38 +  ridge(cumulative_dot_balls) + cluster (id) , data = MDG_2_cut))+ theme(legend.position = "none") + 
  ggtitle("Aalen plot of MD Gunathilaka for the second innings") 

MDGAalenInn <- ggarrange(MDG_p1,MDG_p2, nrow = 2)
MDGAalenInn
```

```{r,warning=FALSE,message=FALSE,results='hide'}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"MDGAalenInn.eps"),width = 10,height = 7,horizontal = FALSE)
MDGAalenInn
dev.off()
```

