---
title: "MDG_POS"
author: "S_16_373"
date: "5/10/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


**Load the libraries**
```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(survival)
library(ggfortify)
library(survminer)
library(rms)
library(dynpred)
library(MASS)
library(CPE)
library(scatterplot3d)
library(plotly)
```
\
\
**Read the data sets**
```{r,warning=FALSE,message=FALSE}
Home <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Home/Home.csv")
Overseas <- read.csv("~/Research/Research---ST426/Data/NewData/Merge/Overseas/Overseas.csv")
```
\
\
**Merge two data sets**
```{r,warning=FALSE,message=FALSE}
data_merge <- rbind(Home , Overseas)
```
\
\
**Filter the data of MD Gunathilaka**
```{r,warning=FALSE,message=FALSE}
bt4 <- data_merge %>% filter(grepl('MD Gunathilaka' , Striker))
```
\
\
***1)Analysis for different batting position***
\
\
```{r,message=FALSE,warning=FALSE}
bt4_ps <- bt4 %>% filter(bat_position == c(1,2))

MDG_diff_pos <- survdiff(Surv(cum_balls , wicket) ~ bat_position, data = bt4_ps)
MDG_diff_pos
```
The p value is greater than 0.05. Therefore no significant difference between the batting positions 1 and 2.

\
\
**batting position 1**
\
\
**Filter the first bat_position**
```{r,warning=FALSE,message=FALSE}
MDG_P_1<- bt4 %>% filter(bat_position == 1)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
cox_MDG_P_1_new <- coxph(Surv(cum_balls , wicket) ~ 
                           cum_runs + cum_doubles +cum_boundaries+ridge(cum_dotBalls), data = MDG_P_1)

summary(cox_MDG_P_1_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_MDG_P_1 <- cox.zph(cox_MDG_P_1_new)
test_MDG_P_1
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_MDG_P_1 <- ggadjustedcurves(cox_MDG_P_1_new , data = MDG_P_1 , size = 2,
                        ggtheme =theme_survminer()) + geom_hline(yintercept = c(0.25,0.5,0.75) ,
                        linetype = "dashed") +ggtitle("Survival curve for MD Gunathilaka for the 1st
                        batting position") + theme(axis.title = element_text(size = 15),axis.text = 
                        element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_MDG_P_1 <- ggforest(cox_MDG_P_1_new , data = MDG_P_1,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_MDG_P_1
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(cum_balls , wicket) ~ 
      cum_runs + cum_doubles +cum_boundaries+ridge(cum_dotBalls), data = MDG_P_1)
```
\
\
**2nd batting position**
\
\
**Filter the second bat_position**
```{r,warning=FALSE,message=FALSE}
MDG_P_2 <- bt4 %>% filter(bat_position == 2)
```
\
\
**Cox model**
```{r,warning=FALSE,message=FALSE}
cox_MDG_P_2_new <- coxph(Surv(cum_balls , wicket) ~ 
                           cum_runs + cum_doubles +cum_boundaries+ridge(cum_dotBalls), data = MDG_P_2)
summary(cox_MDG_P_2_new)
```
\
\
**Test pH assumptions**
```{r,warning=FALSE,message=FALSE}
test_MDG_P_2 <- cox.zph(cox_MDG_P_2_new)
test_MDG_P_2
```
\
\
**Plot the survival curve**
```{r,warning=FALSE,message=FALSE}
cox_plot_MDG_P_2 <- ggadjustedcurves(cox_MDG_P_2_new , data = MDG_P_2 , size = 2,ggtheme = 
                        theme_survminer()) + geom_hline(yintercept = c(0.25,0.5,0.75) , 
                        linetype = "dashed") +ggtitle("Survival curve for MD Gunathilaka for 
                        the 2nd batting position") + theme(axis.title = element_text(size = 15),
                        axis.text = element_text(size = 14))

```
\
\
**coeffient plot**
```{r,message=FALSE,warning=FALSE,fig.dim=c(10,6)}
coef_plot_MDG_P_2 <- ggforest(cox_MDG_P_2_new , data = MDG_P_2,fontsize = 1.2) + 
  theme(axis.title = element_text(size = 15),axis.text = element_text(size = 14))
coef_plot_MDG_P_2
```
\
\
**Area under the curve**
```{r,warning=FALSE,message=FALSE}
AUC(Surv(cum_balls , wicket) ~ 
                           cum_runs + cum_doubles +cum_boundaries+ridge(cum_dotBalls), data = MDG_P_2)
```
\
\
**Survival curve**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,6)}
MDGSurvPlotPos <- ggarrange(cox_plot_MDG_P_1,cox_plot_MDG_P_2,ncol = 2)
MDGSurvPlotPos
```
\
\
**Upload to texStudio**
```{r,results='hide',message=FALSE,warning=FALSE}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"MDGSurvPlotPos.eps"),width = 10,height = 7,horizontal = FALSE)
MDGSurvPlotPos
dev.off()
```
\
\
**Aalen model**
```{r,warning=FALSE,message=FALSE,fig.dim=c(10,7)}
MDG_P_1 <- rename(MDG_P_1,cumulative_runs = cum_runs, cumulative_doubles = cum_doubles,cumulative_fours = 
                    cum_boundaries,cumulative_dot_balls=cum_dotBalls)
MDG_P_2 <- rename(MDG_P_2,cumulative_runs = cum_runs, cumulative_doubles = cum_doubles,cumulative_fours = 
                    cum_boundaries,cumulative_dot_balls=cum_dotBalls)

MDG_p1 <- autoplot(aareg(Surv(cum_balls , wicket) ~ 
                           cumulative_runs + cumulative_doubles +cumulative_fours+ridge(cumulative_dot_balls), data = MDG_P_1)) +
  theme(legend.position = "none") + ggtitle("Aalen plot of MD Gunathilaka for the 1st batting position")

MDG_p2 <- autoplot(aareg(Surv(cum_balls , wicket) ~ 
                           cumulative_runs + cumulative_doubles +cumulative_fours+ridge(cumulative_dot_balls), data = MDG_P_2)) +
  theme(legend.position = "none") + ggtitle("Aalen plot of MD Gunathilaka for the 2nd batting position")

MDGAalenPos <- ggarrange(MDG_p1,MDG_p2, nrow = 2)
MDGAalenPos
```

```{r,warning=FALSE,message=FALSE,results='hide'}
filepath <- "~/Research/Thesis_S16373/images/"
postscript(file = paste0(filepath,"MDGAalenPos.eps"),width = 10,height = 7,horizontal = FALSE)
MDGAalenPos
dev.off()
```

